---
title: "BRT Analysis without 2020"
author: "Anna Talucci"
date: "11/2/2021"
output: html_document
---





# Overview

Drivers of fire refugia in northeaster Siberia fires

## Notes

Boosted Regression Trees in R 
Note: this is a cut-down version of a tutorial prepared by Jane Elith and John Leathwick
Adapted by Chris Dunn for fire risk assessment
Adapted by Garrett Meigs for analysis of fire refugia
Complementary to Krawchuk et al. 2016 Ecosphere scripts



# Clear workspace

```{r}
rm(list=ls()) 
```


## Set libraries
```{r include=FALSE}

library(devtools)
library(gbm)
library(foreign)
library(dismo)
library(dplyr)
library(splines)
library(ggplot2)
```

## BRT functions 
These are provided in a file such as ?brt.functions.R? and can be loaded into R using the source command, e.g.:
```{r}
source("../function/brt.functions.R")
```

# Data
```{r}
model.data = read.csv("../data/CombinedSampledPoints/SampledGEE2001-2020.csv", header=TRUE, sep = ",", strip.white = TRUE)
```


```{r}
model.data
```


## Select Columns 

Response variable Refugia 1 for present, 0 for absent

Explanatory variables
Lat (latitude)
TPI 450 topographic position
Treecover2000 percent tree cover
yedoma present/absent



```{r}
data0119 = model.data %>%
  dplyr::select(classes, latitude, TPI150, TPI450, SLPPCT, aspect, ASPTR, elevation, ruggedness, treecover2000, FireYr) %>%
  filter(FireYr!=2020)

data0119 
```

```{r}
tail(data0119)
```


# Model 1

```{r}
set.seed(15) # Set random seed
brt.model2 <- gbm.step(data=data0119,
    gbm.x = c(2, 3, 4, 5, 6, 7, 8, 9, 10), 
    gbm.y = 1,
    family = "bernoulli",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model output
```{r}
summary(brt.model2,
        cBars=length(brt.model2$var.names),
        n.trees=brt.model2$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model outputs as external object for mapping later or posterity

```{r}
save(brt.model2, file = "../outputs/BRTModelsGEE/BRT2_model.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../outputs/BRTModelsGEE/BRT2_model.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.model2, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)

### Plotting (Anna Added)
```{r}
gbm.plot(brt.model2, smooth=TRUE, write.title = TRUE, y.label="Fitted function", x.label="")
dev.print(pdf, "../outputs/BRTModelsGEE/BRT2_plots.pdf")
dev.off()
```
```{r}
gbm.plot.fits(brt.model2)
dev.print(pdf, "../outputs/BRTModelsGEE/BRT2_fits.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.model2)
find.int$rank.list
find.int$interactions
```

## Calculate outputs stats 
- Sandra Haire calculations and file export below from Krawchuk et al. (2016) Ecosphere
Note that these calculatins are not the same as the default outputss from the BRT code.
```{r}
tot.n=nrow(data0119)
y.perc=round(nrow(data0119[data0119$yvar==1,])/tot.n,2)
vnames=row.names(brt.model2$contributions)
rel.inf=round(brt.model2$contributions[,2],2) # variable num, from df and %contrib for each
perc.dev.expl=round(1-(brt.model2$self.statistics$mean.resid/brt.model2$self.statistics$mean.null),2)
roc.mean=round(mean(brt.model2$cv.roc.matrix),2)
cv.dev.mean=round(brt.model2$cv.statistics$deviance.mean,2)
cv.cor.mean=round(brt.model2$cv.statistics$correlation.mean,2)
cv.discrim.mean=round(brt.model2$cv.statistics$discrimination.mean,2)
```

```{r}
brt.model2.sum=data.frame(tot.n, y.perc, brt.model2$n.trees, perc.dev.expl, roc.mean, cv.dev.mean, cv.cor.mean, cv.discrim.mean)
write.csv(brt.model2.sum, '../outputs/BRTModelsGEE/BRT2_sum.csv', row.names = F)
brt.model2.relinf=data.frame(rel.inf, vnames)
write.csv(brt.model2.relinf, '../outputs/BRTModelsGEE/BRT2_relinf.csv', row.names = F)
```

```{r}
brt.model2.sum
```

```{r}
brt.model2.relinf
```




