---
title: "BRT Partial Plots"
author: "Anna Talucci"
date: "10/7/2021"
output: html_document
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview
Script adapted from Areil Muldoon and Garrett Meigs

September 2019: Extra fun with partial plots.  This script is designed to use brt model runs saved as .Rdas.

Data from BRTAnalysis-SubsetData

# Goal: Overlay partial-dependence plots from multiple models.

NOte: the y-axis of the BRT model are referred to as the fitted function, for a binomial distribtuion this fitted function is the loggit scale. To convert back to a probability we can use the plogis() function. We will leave the y-axix on the logit scale but also add a line for a high probability

setwd("K:/Papers/Meigs_Refugia2_LateSuccessionalForests/r_files_brt")   ### Change to wherever you put the code files sourced below

# Load packages
```{r message=FALSE, warning=FALSE}
library(gbm)
library(dismo)
library(purrr) # for looping
library(ggplot2)
library(scales)
library(dplyr) # for data manip
library(cowplot)
```

# BRT Models


# Load BRT Models 
Load BRT models that are saved during the model as .Rda files in the working directory. Models are assembled and run in the script 'BRTAnalyses'
```{r}
load(file = "../outputs/BRTmodels/BRT1_model.rda")
brt.model1 = brt.model1
```

# Data

```{r}
data = read.csv("../data/CombinedSampledPoints/SampledPoints.csv") 
```

```{r}
head(data)
```

# Manuscript figure

## models 
Make list of models and variables
mods4 = list(Hi_4var = brt.model1, Mod_4var = brt.model2, Full_4var = brt.model6)
vars4 = c("dndmi", "elevation", "fwi", "ndviprefire")
names(vars4) = vars4
vars4
```{r}
mods4 = list(full_mod= brt.model1)
vars4 = c("LAT", "TPI450", "TPI150", "ruggedness", "SLPPCT", "aspect", "ASPTR", "elevation")
names(vars4) = vars4
vars4
```


Nicer variable names for x axis labels Must be in same order as vars
```{r}
x_names4 = c("LAT", "TPI450", "TPI150", "ruggedness", "SLPPCT", "aspect", "ASPTR", "elevation")
```

### Predicted dataset 
Use nested loops for each variable and then each model within each variable

 For outer loop use map() or lapply()
 For the inner loop use imap_dfr() to use models and model names and bind together

 Work out approach with a single variable
 Goal is to get a dataset with predictions from all models stacked together for one x variable

### Loop through single varible
```{r}
pred_test4 = map(vars4[[1]], function(variable) {
     imap_dfr(mods4, function(Model, mod.name) {
          preddat = plot.gbm(Model, i.var = variable, return.grid = TRUE)
          preddat$center_y = scale(preddat$y, scale = FALSE)
          preddat$x = preddat[, 1]
          preddat$Model = mod.name
          preddat
     })
})

pred_test4
```

### Loop through all Varaibles 
If that worked, loop through all variables
```{r}
pred_mods4 = map(vars4, function(variable) {
     imap_dfr(mods4, function(model, mod.name) {
          preddat = plot.gbm(model, i.var = variable, return.grid = TRUE)
          preddat$center_y = scale(preddat$y, scale = FALSE)
          preddat$x = preddat[, 1]
          preddat$model = mod.name
          preddat
     })
})
```

Figure out plot limits (if want all the same) by binding all groups together and calculating min and max center_y
```{r}
range(bind_rows(pred_mods4)$center_y)
```

### Plot with improved x axis names ----
```{r}
model_id <- ggplot(data = pred_mods4[[1]], aes(x = x, y = center_y, linetype = model, color = model) ) +
        geom_smooth(span = 0.5, se = FALSE) + # choose span? 
        scale_color_manual(values = c("blue","red", "orange"), name = "Fire weather", guide = guide_legend(reverse=TRUE)) +
        scale_linetype_manual(values = c("solid", "longdash", "twodash"), name = "Fire weather", guide = guide_legend(reverse=TRUE)) +
        labs(x = x_names4[[1]]) +
        theme_bw(base_size = 12) +
        theme(axis.text.x = element_text(size = 10, color = "black"),
              axis.text.y = element_text(size = 10, color = "black"),
              panel.border = element_rect(color = "black", size = 1.25),
              panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
              legend.position = "bottom",
              legend.title = element_text(size = 14),
              legend.text = element_text(size = 14)) +
        scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
        #scale_x_continuous(labels = comma) +
        #ylim(-1.55, 1.55) +
        geom_hline(yintercept=0)+
        scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.197225,-0.8472979, 0, 0.8472979, 2.197225), labels = c("0.1", "0.3", "0.5", "0.7", "0.9"), name="Probability")

model_id
```
Leaving legend to indicate multiple models plotted.



### Plotting function ----
Note: plot.margin - t,r,b,l

Adjust plot margins for compiling a panel figure with cowplot.

```{r}
pardep_plot_mods4 = function(data, x_var) {
     ggplot(data = data, aes(x = x, y = center_y, linetype = model, color = model) ) +
    geom_smooth(span = 0.5, se = FALSE) + # choose span? 
    scale_color_manual(values = c("blue","red", "orange")) +
                labs(x = x_var) +
                theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(0.05, 0.2, 0.05, 0.5), "cm")) +
                theme(axis.text.x = element_text(size = 10, color = "black"),
                      axis.text.y = element_text(size = 10, color = "black"),
                      panel.border = element_rect(color = "black", size = 1.25),
                      panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
                      legend.position = "none") +
                scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
                scale_x_continuous(labels = comma) +
                #ylim(-1.55, 1.55) +
                geom_hline(yintercept=0)+
                scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.197225,-0.8472979, 0, 0.8472979, 2.197225), labels = c("0.1", "0.3", "0.5", "0.7", "0.9"), name="Probability")
}

pardep_plot_mods4(data = pred_mods4[[1]], x_var = x_names4[[1]])
```

### Loop through the models and the x variable names
    simultaneously with map2()
```{r}
all_mod_plots4 = map2(pred_mods4, x_names4, pardep_plot_mods4)
all_mod_plots4
```




## Manuscript Figure


```{r fig.height=5, fig.width=6}
msplot1 = cowplot::plot_grid( all_mod_plots4$LAT, all_mod_plots4$TPI450, all_mod_plots4$treecover2000, all_mod_plots4$yedoma, ncol = 2) +
    draw_label("lowland", x = .66, y = .62, size = 9) +
   draw_label("upland", x = .94, y = .62, size = 9) +
   draw_label("absence", x = .66, y = .12, size = 9) +
   draw_label("presence ", x = .94, y = .12, size = 9) +
   draw_label("(a)", x = .14, y = .97, size = 10) +
   draw_label("(b)", x = .64, y = .97, size = 10) +
   draw_label("(c)", x = .14, y = .47, size = 10) +
   draw_label("(d)", x = .64, y = .47, size = 10) 

msplot1
```



```{r eval=FALSE, include=FALSE}
ggsave("../figures/PartialPlot.tiff", plot = msplot1, width = 6, height =5, units = c("in"), dpi=600 )
```
**THE END**