---
title: "Class Patch Metrics by fire"
author: "Anna Talucci"
date: "9/16/2021"
output: html_document
---



# Overview

This script process landscape/patch statistics by class burned/unburned for the 2020 fires in Northeastern Siberia. Fires are processed individually.


[Landscapemetrics package details](https://cran.r-project.org/web/packages/landscapemetrics/landscapemetrics.pdf)

## Fire IDobj
Change for each iteration 

IDobj=314

#Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
```

# Data
```{r}
r1 <- raster("../data/dNBRSingleFireBinary/IMG_Binary314.tif")
```

```{r}
r1
```

```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2020.shp", "NESiberiaFires2020")
```



# Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==314)

fire1
```

# Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

# Plot
```{r}
plot(crop_r1)
plot(st_geometry(fire1), add=TRUE)
```

# Define Landscape
```{r}
landscape = crop_r1
```

# Check Landscape for processing
```{r}
check_landscape(landscape)
```

# Visualize landscape
```{r}
show_patches(landscape) 
show_cores(landscape)
```


# Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(., level = "class", full_name = TRUE) %>% 
  mutate(IDobj = 314) %>% 
  write.csv(., '../outputs/PatchSummary/ClassFire314.csv',  row.names = FALSE)
```