---
title: "Combine Patch Data, add fire data, remove scanline fires"
author: "Anna Talucci"
date: "9/20/2021"
output: html_document
---

# Clear workspace

```{r}
rm(list=ls()) 
```

# Overview

# Fires with Scanline Errors
```{r}
target = c(351, 361, 403, 422, 428, 434, 439, 498, 544, 550, 598, 636, 808, 892, 944, 1097, 1190, 1275, 1363, 1416, 1742, 1773, 2135, 2216, 2295,2322, 2346, 2350, 2351, 2358, 2367, 2383, 2466, 2491, 2514, 2722, 2757, 2833, 2905, 3008, 3213)
```

# Packages

```{r}
library(tidyverse)
```

# Define graph Theme and color Palette 

##Themes
```{r}
lb_theme = theme_bw() + theme(legend.position = "bottom") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```

```{r}
bar_theme = theme_bw() + 
  theme(legend.position = "none", legend.title = element_blank()) +
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black")) 
```

```{r}
ecoPalette <- c("#b5b35c", "#556b2f")
```


# Data

## Fire data

```{r}
fires = read.csv("../data/NESiberiaFires/NESiberiaFires2020.csv") 
```

## Class patch summaries


```{r}
csv_patch = list.files(path = '../data/PatchSummaryUTM', pattern = "csv$", full.names = TRUE)
```

```{r include=FALSE}
stacked_patch <- map_dfr(csv_patch, read_csv)
```

# Organize Patch Class Data 
1. Filter - remove fires with scanline error
2. Pivot Wider so each patch metric is a column
```{r}
df1 = stacked_patch %>% 
  filter(!IDobj %in% target) %>%
  pivot_wider(id_cols =  c(IDobj, class), names_from = metric, values_from = value)

```

```{r eval=FALSE, include=FALSE}
unique(df1$IDobj)
```


# Combine Fire data with Patch data

```{r}
data1 = merge(df1, fires, by = "IDobj")
```


```{r}
data2 = data1 %>% 
  mutate(LogHa = log(SizeHa))  %>%
  mutate(Logarea_mn = log(area_mn))  %>%
  dplyr::select(IDobj:class, area_mn, ca,np, enn_mn, para_mn, pd, pland, tca, SizeHa, EcoCode, ArcSub, SizeCl, LogHa, Logarea_mn) 
  
data2
```

```{r}
refugia = data2 %>% 
  filter(class==1) %>%
  mutate(Logca = log(ca))  %>%
  mutate(Logtca = log(tca)) %>%
  mutate(FireSize = ifelse((SizeCl %in% 1:3), "small", 
                      ifelse((SizeCl %in% 4:6), "moderate", "large"))) 

refugia
```
Write refugia data to file
```{r eval=FALSE, include=FALSE}
write.csv(refugia, '../outputs/ClassPatchSummary/Refugia.csv',  row.names = FALSE)
```

```{r}
burnt = data2 %>% 
  filter(class==0) %>%
  mutate(Logca = log(ca))  

burnt
```

# Summaries patch data

Data of interest
- Mean of patch area (Area and edge metric)
- Perimeter-area ratio lsm_c_para_cv
- Percentage of landscape
- Total Core Area

Class
- 0 Burned
- 1 Unburned

Metric
1. area_mn
2. ca
3. enn (distance)
4. np
5. para (perimeter area ratio)
6. pd
7. pland
8. tca

```{r}

refugia %>%
  group_by(as.factor(SizeCl)) %>%
  summarise(n=n())
```
## Tables


```{r}
refugia %>% 
  group_by(EcoCode, ArcSub) %>%
  summarise(mean_area = mean(area_mn),
            sd_area = sd(area_mn),
            mean_ca = mean(ca),
            sd_ca = sd(ca),
            mean_enn = mean(enn_mn),
            sd_enn = sd(enn_mn),
            mean_pd= mean(pd),
            sd_pd= sd(pd),
            mean_pland = mean(pland),
            sd_pland = sd(pland),
            mean_tca = mean(tca),
            sd_tca = sd(tca)) %>%
   write.csv(., '../outputs/ClassPatchSummary/Table1.csv',  row.names = FALSE)


```

```{r}
refugia %>%
  group_by(as.factor(SizeCl)) %>%
  summarise(sum = sum(SizeHa))
  

```

ifelse(SizeHa %in% 200:499, "1",
                  ifelse(SizeHa %in% 500:999, "2",
                   ifelse(SizeHa %in% 1000:1999, "3",
                       ifelse(SizeHa %in% 2000:4999, "4",
                         ifelse(SizeHa %in% 5000:9999, "5",
                            ifelse(SizeHa %in% 10000:19999, "6",
                              ifelse(SizeHa %in% 20000:49999, "7",
                                ifelse(SizeHa %in% 50000:99999, "8", "9")))))))))
                                
Small 200-1999 ha
Moderate 2000-19,999 ha
Large 20,000-
```{r}
refugia %>%
  group_by(FireSize) %>%
  summarise(sum = sum(SizeHa)) %>%
  write.csv(., '../outputs/ClassPatchSummary/Table14.csv',  row.names = FALSE)


```

```{r}
refugia %>% 
  group_by(ArcSub, FireSize) %>% 
  summarise(mean=mean(area_mn), 
            sd=sd(area_mn), 
            min=min(area_mn), 
            max=max(area_mn))
```

### Fires Patch Figure

```{r}
target_patch = c(601, 673, 872, 885, 1166, 1327)
```

```{r}

data2 %>% 
  filter(IDobj %in% target_patch) %>%
   mutate(mean_tca_patch = tca/np) %>%
  mutate(radiusTca = sqrt(((mean_tca_patch*10000)/3.14))) %>%
  dplyr::select(IDobj:area_mn, enn_mn, tca, mean_tca_patch, radiusTca, np, SizeHa:SizeCl) %>%
  write.csv(., '../outputs/ClassPatchSummary/PatchFigEnnTca.csv',  row.names = FALSE)


 
```

```{r}

data2 %>% 
  filter(IDobj %in% target_patch) %>%
   mutate(mean_tca_patch = tca/np) %>%
  mutate(radiusTca = sqrt(((mean_tca_patch*10000)/3.14))) %>%
  group_by(class) %>%
  dplyr::select(class, enn_mn, tca, mean_tca_patch, radiusTca) %>%
 summarise(across(everything(), list(mean=mean, sd=sd, min = min, max = max))) %>%
 
  write.csv(., '../outputs/ClassPatchSummary/PatchFigSum.csv',  row.names = FALSE)


 
```

```{r}

data2 %>% 
   mutate(mean_tca_patch = tca/np) %>%
  mutate(radiusTca = sqrt(((mean_tca_patch*10000)/3.14))) %>%
  group_by(class, EcoCode, ArcSub) %>%
  dplyr::select(class, EcoCode, ArcSub, enn_mn, tca, mean_tca_patch, radiusTca) %>%
 summarise(across(everything(), list(mean=mean, sd=sd, min = min, max = max))) %>%
 
  write.csv(., '../outputs/ClassPatchSummary/PatchDisEcoArcSum.csv',  row.names = FALSE)


 
```

```{r}

data2 %>% 
   mutate(mean_tca_patch = tca/np) %>%
  mutate(radiusTca = sqrt(((mean_tca_patch*10000)/3.14))) %>%
  dplyr::select(IDobj:area_mn, enn_mn, tca, mean_tca_patch, radiusTca, np, SizeHa:SizeCl) 


 
```

```{r}
data2 %>% 
   mutate(mean_tca_patch = tca/np) %>%
  mutate(radiusTca = sqrt(((mean_tca_patch*10000)/3.14))) %>%
  group_by(class) %>%
  dplyr::select(class, enn_mn, tca, mean_tca_patch, radiusTca) %>%
 summarise(across(everything(), list(mean=mean, sd=sd, min = min, max = max))) %>%
  write.csv(., '../outputs/ClassPatchSummary/EnnTcaRadiusSumAll.csv',  row.names = FALSE)
```
### Summary Means by EcoCode and Class
```{r}
data2 %>% 
  group_by(EcoCode, class) %>%
  summarise(MeanArea = mean(area_mn),
            MeanCa = mean(ca),
            MeanNp = mean(np),
            MeanEnn = mean(enn_mn),
            MeanPara = mean(para_mn),
            MeanPd=mean(pd),
            MeanPland = mean(pland),
            MeanTca = mean(tca))

```
### Summary Means by EcoCode, Class, ArcSub
```{r}
data2 %>% 
  dplyr::select(IDobj:class, area_mn, ca,np, enn_mn, para_mn, pd, pland, tca, SizeHa, EcoCode, ArcSub, SizeCl) %>%
  group_by(EcoCode, ArcSub, class) %>%
  summarise(MeanArea = mean(area_mn),
            MeanCa = mean(ca),
            MeanNp = mean(np),
            MeanEnn = mean(enn_mn),
            MeanPara = mean(para_mn),
            MeanPd=mean(pd),
            MeanPland = mean(pland),
            MeanTca = mean(tca)) %>%
   write.csv(., '../outputs/ClassPatchSummary/Table2.csv',  row.names = FALSE)

```

### Summary Means by EcoCode and Size Class
```{r}
data2 %>% 
  dplyr::select(IDobj:class, area_mn, ca,np, enn_mn, para_mn, pd, pland, tca, SizeHa, EcoCode, ArcSub, SizeCl) %>%
  group_by(EcoCode, SizeCl) %>%
  summarise(MeanArea = mean(area_mn),
            MeanCa = mean(ca),
            MeanNp = mean(np),
            MeanEnn = mean(enn_mn),
            MeanPara = mean(para_mn),
            MeanPd=mean(pd),
            MeanPland = mean(pland),
            MeanTca = mean(tca)) %>%
   write.csv(., '../outputs/ClassPatchSummary/Table3.csv',  row.names = FALSE)


```

### Refugia
```{r}
sum1 = refugia %>%
  dplyr::select(IDobj, tca, SizeHa, EcoCode) %>%
  group_by(EcoCode) %>%
  summarise(sum_tca = sum(tca),
            sum_SizeHa = sum(SizeHa)) %>%
  mutate(percentCoreArea = (sum_tca/sum_SizeHa)*100)

sum1
```
Area For NST
```{r}
sum1 %>% filter(EcoCode=="NST") %>%
  mutate(percentBurned = sum_SizeHa/(1133262*100)*100)

```

Area for CKMT
```{r}
sum1 %>% filter(EcoCode=="CKMT") %>%
  mutate(percentBurned = sum_SizeHa/(560461*100)*100)

```


# Graphs
```{r}
data2
```

## Mean patch area by class
```{r}
ggplot(data2, aes(x=as.factor(class), y=Logarea_mn, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = ecoPalette, name="Ecozone") +
    xlab("Fire Size Class") +
      ylab("Mean percent ") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

```{r}
ggplot(refugia, aes(x=as.factor(class), y=Logarea_mn, fill=as.factor(SizeCl))) + 
    geom_boxplot() + 
    xlab("Fire Size Class") +
      ylab("Mean patch size ") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```
`

```{r}
ggplot(refugia, aes(x=as.factor(class), y=pd, fill=as.factor(SizeCl))) + 
    geom_boxplot() + 
    xlab("Fire Size Class") +
      ylab("patch density") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```
```{r}
data2
```
# Refugia Graphs
## Boxplots

### Patch Density
```{r}
density_plot = ggplot(refugia, aes(x=ArcSub, y=pd, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = ecoPalette) +
    xlab("") +
      ylab("Patch density per 100 ha per fire") +
  bar_theme +
  theme(legend.position = c(.15, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=1), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 

density_plot
```


### Percent Landscape
```{r}
ggplot(refugia, aes(x=EcoCode, y=pland, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = ecoPalette, name="Ecozone") +
    xlab("ecozones") +
      ylab("percent landscape") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

### Percent Landscape (Arctic/Sub)
```{r}
ggplot(refugia, aes(x=ArcSub, y=pland, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = ecoPalette, name="Ecozone") +
    xlab("ecozones") +
      ylab("percent landscape") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

### Patch Size
```{r}
size_plot = ggplot(refugia, aes(x=ArcSub, y=Logarea_mn, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = ecoPalette) +
    xlab("") +
      ylab("Mean patch size in ha per fire\n(log transformed)") +
  bar_theme +
  theme(legend.position = c(.15, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=1), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 

size_plot
```

### Class area
```{r}
ggplot(refugia, aes(x=EcoCode, y=Logca, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = ecoPalette, name="Ecozone") +
    xlab("ecozones") +
      ylab("class area (Log transformed)") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

### Number of Patches
```{r}
ggplot(refugia, aes(x=EcoCode, y=np, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = ecoPalette, name="Ecozone") +
    xlab("ecozones") +
      ylab("number of patches") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

### Patch Density
```{r}
ggplot(refugia, aes(x=EcoCode, y=para_mn, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = ecoPalette, name="Ecozone") +
    xlab("ecozones") +
      ylab("perimeter-area ratio") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

### Total Core Area
```{r}
ggplot(refugia, aes(x=EcoCode, y=tca, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = ecoPalette, name="Ecozone") +
    xlab("ecozones") +
      ylab("class area (Log transformed)") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

## Scatter Plots
### Fire Size by class area (log transformed)*
```{r fig.height=4, fig.width=6}
plot1 = ggplot(refugia, aes(x=LogHa, y=Logca, color=as.factor(EcoCode))) + 
    geom_point() + 
  scale_color_manual(values = ecoPalette, name="Ecozone") +
    xlab("Total fire area\n(log transformed)") +
      ylab("Total Fire refugia area in ha\n(Log Transformed)") +
  theme(legend.position = c(.9, .15),
        legend.key.height = unit(.25, 'in'), 
        legend.key.width = unit(.25, 'in'),
        legend.background = element_rect(fill='white')) + 
  theme(legend.text = element_text(size = 8)) 

plot1
```
```{r}
ggsave("../figures/Plot1.png", plot = plot1, width = 6, height = 4, units = c("in"), dpi = 600)
```

### Patch Density by mean patch size*
```{r fig.height=4, fig.width=6}
plot2 = ggplot(refugia, aes(x=Logarea_mn, y=pd, color=as.factor(EcoCode))) + 
    geom_point() + 
  
  scale_color_manual(values = ecoPalette, name="Ecozone") +
    xlab("Patch Size in ha\n(log transformed)") +
      ylab("Patch Density\n(count per 100 ha)") +
  theme(legend.position = c(.9, .9),
        legend.key.height = unit(.25, 'in'), 
        legend.key.width = unit(.25, 'in'),
        legend.background = element_rect(fill='white')) + 
  theme(legend.text = element_text(size = 8)) 

plot2
```
```{r}
ggsave("../figures/plot2.png", plot = plot2, width = 6, height = 4, units = c("in"), dpi = 600)
```
### Patch Density by mean patch size
```{r}
ggplot(refugia, aes(x=Logarea_mn, y=para_mn, color=as.factor(EcoCode))) + 
    geom_point() + 
  
  scale_color_manual(values = ecoPalette, name="Ecozone") +
    xlab("Patch Size (ha; log transformed)") +
      ylab("Perimeter area ratio") +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

## Class area and Fire Size*
```{r fig.height=4, fig.width=6}
plot3 = ggplot(burnt, aes(x=pland, y=Logarea_mn, color=as.factor(EcoCode))) + 
    geom_point() + 
  scale_color_manual(values = ecoPalette, name="Ecozone") +
    xlab("Percent area of fire refugia") +
      ylab("Patch size in ha\n(log transformed)") +
  theme(legend.position = c(.9, .15),
        legend.key.height = unit(.25, 'in'), 
        legend.key.width = unit(.25, 'in'),
        legend.background = element_rect(fill='white')) +  
  theme(legend.text = element_text(size = 8)) 

plot3
```
```{r}
ggsave("../figures/Plot3.png", plot = plot3, width = 6, height = 4, units = c("in"), dpi = 600)
```
### Patch Size by Total Core Area
```{r}
ggplot(refugia, aes(x=enn_mn, y=Logarea_mn, color=as.factor(EcoCode))) + 
    geom_point() + 
  
  scale_color_manual(values = ecoPalette, name="Ecozone") +
    xlab("Total core area") +
      ylab("Patch Size (ha; log transformed)") +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

## Others
```{r}
ggplot(refugia, aes(x=EcoCode, y=pd, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = ecoPalette, name="Ecozone") +
    xlab("ecozones") +
      ylab("patch density") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

```{r}
ggplot(refugia, aes(x=EcoCode, y=Logarea_mn, fill=as.factor(SizeCl))) + 
    geom_boxplot() + 
    xlab("Fire Size Class") +
      ylab("Mean patch Size ") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

```{r}
ggplot(refugia, aes(x=EcoCode, y=Logca, fill=as.factor(SizeCl))) + 
    geom_boxplot() + 
    xlab("Fire Size Class") +
      ylab("Unburned area") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

```{r}
ggplot(burnt, aes(x=EcoCode, y=Logca, fill=as.factor(SizeCl))) + 
    geom_boxplot() + 
    xlab("Fire Size Class") +
      ylab("burnt area") +
  bar_theme +
  theme(legend.position = c(.5, .05),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=2), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 
```

## Subset of fires
```{r}
target = c(1327, 1042, 2833, 1692, 1062, 2334, 1693, 1166, 1559, 958, 885,977, 1704, 1322, 601, 872, 894, 673)

```

```{r}
refugia %>% filter(IDobj %in% target)
```

# Combined Plots

```{r fig.height=4, fig.width=6}
fig1 = cowplot::plot_grid(size_plot, density_plot)
fig1
```
```{r eval=FALSE, include=FALSE}
ggsave("../figures/PatchSizeDensity.tiff", plot = fig1, width = 6, height =4, units = c("in"), dpi=600 )
```

**THE END**

