---
title: "Combine sample points into one file"
author: "Anna Talucci"
date: "9/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Combine sampled data points from Raster to Point conversion. Points are grouped by UTM zone. Combine points form same UTM zone and add Row ID column, to distinguish each point. Add UTM zone column as well. 
# Packages
```{r}
library(tidyverse)
library(sf)
library(mapedit)
```



# Define folder and file details
```{r}
poly_folder <- "../data/RasterToPointUTM/UTM58" 

    #--store shapefile names as a list
poly_shp_files <- list.files(poly_folder, pattern = "\\.shp$")
```

```{r}
poly_shp_files

```



```{r}
# Reads in all shapefiles from Directory that include the string "_CDs".
poly_files <- list.files(poly_folder , pattern="\\.shp$", full.names=TRUE)
```

```{r}
poly_files
```

# Function to read all shapefiles into list
```{r}

st_read_poly_shp <- function(shp_list) {

      layer_name <- as.character(gsub(".shp","",shp_list))

      shp_st_read <-st_read(dsn = poly_folder, layer = layer_name)


    }
```



```{r}
shp_list=poly_shp_files[[1]]
shp_list
```

```{r}
layer_name <- as.character(gsub(".shp","",shp_list))

st_read(dsn = poly_folder, layer = layer_name)
```

```{r}
 poly_shp_list <- lapply(poly_shp_files, st_read_poly_shp)
```

# Take list and combine into single shapefile
```{r}
all_data <- sf::st_as_sf(data.table::rbindlist(poly_shp_list))
```


# Check data
```{r}
all_data
```

# Add atributes
# Remove scanline by IDobj
```{r}
target = c(471, 516, 585, 705, 793, 826, 931, 941, 977, 1014, 1042, 1145, 1217, 1238, 1239, 1289, 1290, 1333, 1451, 1529, 1619, 1672, 1693, 1704, 1744, 1970, 2050, 2104, 2134, 2205, 2239, 2592, 2866, 3144, 3880, 3902)
```


```{r}
df1 = all_data %>% 
  filter(!IDobj %in% target) %>%
  mutate(BurnUnburn = ifelse(between(dnbr, -100, 0), "unburned", 
                      ifelse(between(dnbr,0, 100), "unburned", "burned"))) %>%
  mutate(UTMZone = 58) %>%
  tibble::rowid_to_column(., "ID") %>% 
  dplyr::select(ID, IDobj, UTMZone, dnbr, BurnUnburn, geometry)

df1
  
```


# Sample size in each UTM group
```{r}
df1 %>%
  group_by(UTMZone,BurnUnburn) %>%
  summarise(n=n())

```

# Reduce Sample size

```{r}
set.seed(101)
samplePt = df1 %>% 
  group_by(BurnUnburn, IDobj) %>%
  sample_frac(0.05)

```

```{r}
samplePt %>% 
  group_by(UTMZone,BurnUnburn) %>%
  summarise(n=n())
```


# Write to Shapefile
```{r}
st_write(samplePt, "../outputs/SamplePoints/Sample5of5UTM58.shp", driver="ESRI Shapefile") 
```
