---
title: "difference test"
author: "Anna Talucci"
date: "10/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview


# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(lme4)
library(cowplot)
library(lme4)
library(lsmeans)
library(DHARMa)
library(multcomp)
library(car)
library(grid)
library(gtable)
library(gridExtra)
library(gmodels)
```


# Data

```{r}
refugia = read.csv("../data/ClassPatchSummary/Refugia.csv") 
```

```{r}
seed = read.csv("../data/ClassPatchSummary/DispersalEstimatesFire.csv") 
```
# Define graph Theme and color Palette 

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```

```{r}

reg_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

```{r}
bar_theme = theme_bw() + 
  theme(legend.position = "none", legend.title = element_blank()) +
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black")) 
```

```{r}
ecoPalette <- c("#b5b35c", "#556b2f")
```

```{r}
cbEcoPal = c("#E1BE6A", "#40B0A6")
```

# Summary stats
```{r}
refugia %>% 
  group_by(ArcSub, FireSize) %>% 
  summarise(n = n(),
            mean=mean(area_mn), 
            sd=sd(area_mn), 
            min=min(area_mn), 
            max=max(area_mn))
```

```{r}
refugia = refugia %>%
  mutate(FireSize2 = factor(FireSize, levels = c("small", "moderate", "large")))
```

```{r}
refugia

```
## Box plots
```{r fig.height=2.3, fig.width=3}
size_plot = ggplot(refugia, aes(x=ArcSub, y=area_mn, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = cbEcoPal) +
  scale_y_continuous(trans='log10') +
  scale_x_discrete(labels=c("arctic" = "Arctic", "subarctic" = "Subarctic")) +
    xlab("") +
      ylab("Mean fire refugia\nsize per fire in ha") +
  bar_theme +
  theme(legend.position = c(.15, .93),
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=1), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 



size_plot
```
## Density
```{r fig.height=2.3, fig.width=3}
density_plot = ggplot(refugia, aes(x=ArcSub, y=pd, fill=EcoCode)) + 
    geom_boxplot() + 
   scale_fill_manual(values = cbEcoPal) +
    xlab("") +
      ylab("Fire refugia density per\nfire (count per 100 ha)") +
  scale_x_discrete(labels=c("arctic" = "Arctic", "subarctic" = "Subarctic")) +
  bar_theme +
  theme(legend.position = "none",
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0))) + 
  guides(fill = guide_legend(ncol=1), 
         shape = guide_legend(override.aes = list(size = 0.4)), 
         color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.text = element_text(size = 8)) 



density_plot
```

# Analysis


## Patch Size Large vs medium, vs small fires
```{r}
fit2 = lm(area_mn ~ FireSize2, data = refugia)
```

#### Residuals
```{r}
# Get the fitted value for each observation
refugia$fit2 = fitted(fit2)
# Get the residuals of the model
refugia$res2 = residuals(fit2)
```

```{r}
qplot(x = fit2, y = res2, data = refugia,
main = "Residuals vs Fitted Values")
```

```{r}
qplot(x = FireSize, y = res2, data = refugia,
xlab = "size class group",
ylab = "Residuals",
main = "Residuals vs burn/unburn")
```
```{r}
qplot(x = factor(1), y = res2, data = refugia, geom = "boxplot")
```

```{r}
qqnorm(refugia$res2, main = "Normal QQ Plot of Residuals")
qqline(refugia$res2) # add reference line to the qq plot
```

```{r}
plot(fit2, which = 1) # residual vs fitted values
```

```{r}
plot(fit2, which = 2) # qqnorm plot of residuals
```

#### Summary
```{r}
summary(fit2)
```
```{r}
anova(fit2)
```


```{r}
# All the coefficients
coef(fit2)
```

```{r}
# All the confidence intervals for the coefficients
confint(fit2)
```

```{r}
small = c(1, 0, 0) 
medium = c(1, 1, 0) 
large = c(1, 0, 1)
```

```{r}
# Create vectors for treatment comparisons with subtraction
small_large = small-large
medium_large = medium-large
small_medium = small-medium
```

```{r}
 # Stack the differences in means vectors together
(diffest2 = rbind(small_large, medium_large, small_medium) )
```

```{r}
( estdiffdate2 = estimable(fit2, diffest2, conf.int = .983) )
```
```{r}
estdiffdate2$group = factor(rownames(estdiffdate2),
levels = c("small_large", "medium_large", "small_medium"),
labels = c("Small vs Large", "Medium vs Large", "Small vs Medium"))
```

```{r}
write.csv(estdiffdate2, '../outputs/Analysis/FireSizeDifference.csv',  row.names = FALSE)
```
### plots

```{r fig.height=4, fig.width=6}
( g1 = ggplot(estdiffdate2, aes(x = group, y = Estimate) ) + # Set axes
geom_errorbar(width = .1, lwd = .75, aes(ymin = Lower.CI, ymax = Upper.CI)) + # Add error bars geom_point(size = 3) + # Add point estimate, change point size
geom_hline(yintercept = 0, color="grey34") + # Add horizontal line at 0
geom_hline(yintercept = c(.25, -.25), color = "grey34", lty = 4) + # Add horiz line at +/-.25 theme_bw() + # change graph to black and white for printing
xlab(NULL) + ylab("Patch size (ha)") + # Change axis labels
theme(panel.grid.major.x = element_blank() ) )


```

### Figure
```{r fig.height=2.3, fig.width=3}
(g2 = ggplot(estdiffdate2, aes(x = Estimate, y = group) ) +

   geom_errorbarh(height = .1, lwd = .75, aes(xmin = Lower.CI, xmax = Upper.CI)) + 
  geom_point(size = 3) + 

  geom_vline(xintercept = 0, lty = 2) + 

  geom_rect(alpha = .05, aes(xmin = -1, xmax = 1, ymin = 0, ymax = 4) ) +

theme_bw() +
ylab("") + xlab("Difference in mean fire refugia size (ha)") + 
theme(axis.ticks.y = element_blank(),
axis.text.y = element_blank(),
axis.title.x = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black")) + 
  theme(panel.grid.major.y = element_blank() ) + 
  
  geom_text(aes(x = Estimate, y = as.numeric(group) + .3,
label = group), size = 3) + 
  annotate("text", x = 0, y = .3, label = "Zone of\nno difference", size = 2) )

```


```{r}
ggsave("../figures/FireSizeDifference.png", plot = g2, width = 6, height = 4, units = c("in"), dpi = 600)
```

## Density

```{r}
mod2 = lm(pd ~ FireSize2, data = refugia)
```




#### Summary
```{r}
summary(mod2)
```
```{r}
anova(mod2)
```

```{r}
small2 = c(1, 0, 0) 
medium2 = c(1, 1, 0) 
large2 = c(1, 0, 1)
```

```{r}
# Create vectors for treatment comparisons with subtraction
small_large2 = small2-large2
medium_large2 = medium2-large2
small_medium2 = small2-medium2
```

```{r}
 # Stack the differences in means vectors together
(diffestmod2 = rbind(small_large2, medium_large2, small_medium2) )
```

```{r}
( estdiffdatemod2 = estimable(mod2, diffestmod2, conf.int = .983) )
```
```{r}
estdiffdatemod2$groupmod2 = factor(rownames(estdiffdatemod2),
levels = c("small_large2", "medium_large2", "small_medium2"),
labels = c("Small vs Large", "Medium vs Large", "Small vs Medium"))
```

```{r}
write.csv(estdiffdatemod2, '../outputs/Analysis/FireDensityDifference.csv',  row.names = FALSE)
```
### plots
```{r fig.height=4, fig.width=6}
( f1 = ggplot(estdiffdatemod2, aes(x = groupmod2, y = Estimate) ) + # Set axes
geom_errorbar(width = .1, lwd = .75, aes(ymin = Lower.CI, ymax = Upper.CI)) + # Add error bars geom_point(size = 3) + # Add point estimate, change point size
geom_hline(yintercept = 0, color="grey34") + # Add horizontal line at 0
geom_hline(yintercept = c(.25, -.25), color = "grey34", lty = 4) + # Add horiz line at +/-.25 theme_bw() + # change graph to black and white for printing
xlab(NULL) + ylab("") + # Change axis labels
theme(panel.grid.major.x = element_blank() ) )


```

### Figure

```{r fig.height=2.3, fig.width=3}
(f2 = ggplot(estdiffdatemod2, aes(x = Estimate, y = groupmod2) ) +

   geom_errorbarh(height = .1, lwd = .75, aes(xmin = Lower.CI, xmax = Upper.CI)) + 
  geom_point(size = 3) + 

  geom_vline(xintercept = 0, lty = 2) + 

  geom_rect(alpha = .05, aes(xmin = -1, xmax = 1, ymin = 0, ymax = 4) ) +

theme_bw() +
ylab("") + xlab("Difference in fire refugia density") + 

theme(axis.ticks.y = element_blank(),
axis.text.y = element_blank(),
axis.title.x = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black")) + 
  theme(panel.grid.major.y = element_blank() ) + 
  geom_text(aes(x = Estimate, y = as.numeric(groupmod2) + .3,
label = groupmod2), size = 3) + 
  annotate("text", x = 0, y = .3, label = "Zone of\nno difference", size = 2) )

```



```{r eval=FALSE, include=FALSE}
mod1p = glm(pd ~ FireSize2, data = refugia, family = poisson(link = "log") )
```
mod1nb = glm.nb(numspp ~ size + dist, data = mangrove)

sum(residuals(mod1p, type="pearson")^2)/mod1p$df.res

qplot(fitted(mod1p), resid(mod1p)) + theme_bw()

## Linear modelPatch Density by mean patch size

```{r}
fit3 = lm(Logarea_mn ~ pd, data = refugia)
```

```{r}
linear.model <-lm(pd ~ area_mn, data = refugia)
log.model <-lm(log(pd) ~ area_mn, data = refugia)
exp.model <-lm(pd ~ exp(area_mn), data = refugia)
```


```{r}

summary(log.model)
```


#### Residuals
```{r}
# Get the fitted value for each observation
refugia$fit3 = fitted(fit3)
# Get the residuals of the model
refugia$res3 = residuals(fit3)
```

```{r}
qplot(x = fit3, y = res3, data = refugia,
main = "Residuals vs Fitted Values")
```

```{r}
qplot(x = Logarea_mn, y = res3, data = refugia,
xlab = "Patch area (log transformed",
ylab = "Residuals",
main = "Residuals vs burn/unburn")
```
### Summary datatable
```{r}
summary(log.model)
```

```{r}
summary(log.model)$r.squared 
```
### Data for figure
```{r eval=FALSE, include=FALSE}
uppersize = with(log.model, fit + 2*se.fit) 
lowersize = with(log.model, fit - 2*se.fit)
```
```{r}
log.model.df <- data.frame(x = refugia$area_mn,
                           y = exp(fitted(log.model)))
                          

log.model.df
```

```{r}
ggplot(refugia, aes(x=area_mn, y=pd)) + 
  geom_point() +
  geom_smooth(method="lm", aes(color="Exp Model"), formula= (y ~ exp(x)), se=FALSE, linetype = 1) +
  geom_line(data = log.model.df, aes(x, y, color = "Log Model"), size = 1, linetype = 2) + 
  guides(color = guide_legend("Model Type"))
```
### Patch Density by mean patch size*

  geom_line(data = log.model.df, aes(x, y),color = "#006CD1", size = 1, linetype = 1) +
  
### Figure
```{r fig.height=2.3, fig.width=3}
plot2 = ggplot(refugia, aes(x=area_mn, y=pd)) + 
    geom_point(size=1.5, shape=1, color= "grey50")  + 
    xlab("Fire refugia size (ha)") +
      ylab("Fire refugia density\n(count per 100 ha)") +
  reg_theme 
  

plot2
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/PatchDensityPatchSize.png", plot = plot2, width = 6, height = 4, units = c("in"), dpi = 600)
```

## Linear model Dispersal



```{r}
linear.model4 <-lm(radiusTca ~ area_mn, data = seed)
log.model4 <-lm(log10(radiusTca) ~ area_mn, data = seed)
exp.model4 <-lm(radiusTca ~ exp(area_mn), data = seed)
```


```{r}
summary(linear.model4)
summary(log.model4)
summary(exp.model4)
```


#### Residuals
```{r}
# Get the fitted value for each observation
seed$linear.model4 = fitted(linear.model4)
# Get the residuals of the model
seed$linear.model4 = residuals(linear.model4)
```

```{r}
qplot(x = linear.model4, y = linear.model4, data = seed,
main = "Residuals vs Fitted Values")
```

```{r}
qplot(x = area_mn, y = linear.model4, data = seed,
xlab = "Patch area",
ylab = "Residuals",
main = "Residuals vs burn/unburn")
```

```{r eval=FALSE, include=FALSE}
uppersize = with(linear.model4, fit + 2*se.fit) 
lowersize = with(linear.model4, fit - 2*se.fit)
```
```{r}
linear.model4.df <- data.frame(x = seed$area_mn,
                           y = (fitted(linear.model4)))
                          

linear.model4.df
```

```{r}
ggplot(refugia, aes(x=area_mn, y=pd)) + 
  geom_point() +
  geom_smooth(method="lm", aes(color="Exp Model"), formula= (y ~ exp(x)), se=FALSE, linetype = 1) +
  geom_line(data = log.model.df, aes(x, y, color = "Log Model"), size = 1, linetype = 2) + 
  guides(color = guide_legend("Model Type"))
```

### Dispersal by mean patch size*
```{r}
seed
```

geom_line(data =linear.model4.df, aes(x, y),color = "#006CD1", size = 1, linetype = 1) + 

### Figure
```{r fig.height=2.3, fig.width=3}
dis2 = ggplot(seed, aes(x=area_mn, y=radiusTca)) + 
    geom_point(size=1.5, shape=1, color= "grey50")  +
  
    xlab("Fire refugia size (ha)") +
      ylab("Distance to unburned\nacross burned area (m)") +
  reg_theme

dis2
```
# Combine plots

```{r fig.height=7, fig.width=6}

fig1 = cowplot::plot_grid(size_plot, density_plot, g2, f2, plot2, dis2,   ncol=2)
fig1
```

```{r fig.height=7, fig.width=6}

fig2 = fig1 +
  draw_label("(a)", x = 0.03, y = .99, fontfamily = "sans", fontface = "bold", color = "black", size = 12) +
   draw_label("(b)", x = 0.52, y = .99, fontfamily = "sans", fontface = "bold", color = "black", size = 12) +
  draw_label("(c)", x = 0.03, y = .65, fontfamily = "sans", fontface = "bold", color = "black", size = 12) +
  draw_label("(d)", x = 0.52, y = .65, fontfamily = "sans", fontface = "bold", color = "black", size = 12) +
  draw_label("(e)", x = 0.03, y = .32, fontfamily = "sans", fontface = "bold", color = "black", size = 12) +
  draw_label("(f)", x = 0.52, y = .32, fontfamily = "sans", fontface = "bold", color = "black", size = 12) 

fig2
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/ComboSizeDenistyPatchDiff.png", plot = fig2, width = 6, height = 7, units = c("in"), dpi = 600)
```