---
title: "Field Data Spatial"
author: "Anna Talucci"
date: "6/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Clear workspace

```{r}
rm(list=ls()) 
```

# Overview

# Packacges
```{r, include=FALSE}
library(sp) # spatial data
library(rgdal) # geospatial data
library(raster) # deals with rasters
library(ggplot2)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(tidyr)
library(dplyr)
library(latticeExtra)
library(sf)
```

# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 
+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 

```{r}
ea_ru = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 "
```


# Field data

```{r}
roots = read.csv("../data/FieldSubset/Roots.csv")
```


# Define coordinates
```{r}
rt_cords = cbind(roots$longitude, roots$latitude)
```

# Create  Points  Data Frame
```{r}
data_pt <- SpatialPointsDataFrame(rt_cords, proj4string = CRS(wgs_proj), data = roots)
```

# Transform to Equal area projection
```{r}
data_pt_ea <- spTransform(data_pt, CRS(ea_ru))
```

# Convert from sp to sf
```{r}
data_pt_ea_sf = st_as_sf(data_pt_ea)
```

## Write to shape file

Points
```{r eval=FALSE, include=FALSE}
st_write(data_pt_ea_sf, "../outputs/FieldSpatial/RootsPoints.shp", driver="ESRI Shapefile") 
```
