---
title: "Patch Metrics By Fire UTM 56"
author: "Anna Talucci"
date: "1/31/2022"
output: html_document
---

# Overview

This script process landscape/patch statistics by class burned/unburned **For Each patch** for the 2020 fires in Northeastern Siberia. Fires are processed individually.


[Landscapemetrics package details](https://cran.r-project.org/web/packages/landscapemetrics/landscapemetrics.pdf)

For UTM zone 56 fire


# 331
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_331.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==331)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 331) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_331.csv',  row.names = FALSE)
```

# 370
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_370.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==370)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 370) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_370.csv',  row.names = FALSE)
```


# 371
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_371.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==371)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 371) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_371.csv',  row.names = FALSE)
```


# 381
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_381.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==381)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 381) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_381.csv',  row.names = FALSE)
```


# 390
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_390.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==390)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 390) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_390.csv',  row.names = FALSE)
```


# 399
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_399.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==399)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 399) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_399.csv',  row.names = FALSE)
```


# 413
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_413.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==413)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 413) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_413.csv',  row.names = FALSE)
```


# 415
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_415.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==415)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 415) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_415.csv',  row.names = FALSE)
```


# 416
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_416.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==416)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 416) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_416.csv',  row.names = FALSE)
```


# 425
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_425.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==425)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 425) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_425.csv',  row.names = FALSE)
```


# 431
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_431.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==431)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 431) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_431.csv',  row.names = FALSE)
```


# 450
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_450.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==450)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 450) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_450.csv',  row.names = FALSE)
```


# 454
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_454.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==454)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 454) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_454.csv',  row.names = FALSE)
```


# 459
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_459.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==459)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 459) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_459.csv',  row.names = FALSE)
```


# 462
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_462.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==462)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 462) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_462.csv',  row.names = FALSE)
```


# 474
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_474.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==474)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 474) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_474.csv',  row.names = FALSE)
```


# 476
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_476.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==476)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 476) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_476.csv',  row.names = FALSE)
```


# 478
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_478.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==478)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 478) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_478.csv',  row.names = FALSE)
```


# 479
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_479.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==479)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 479) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_479.csv',  row.names = FALSE)
```


# 483
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_483.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==483)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 483) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_483.csv',  row.names = FALSE)
```


# 485
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_485.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==485)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 485) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_485.csv',  row.names = FALSE)
```

# 500
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_500.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==500)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 500) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_500.csv',  row.names = FALSE)
```

# 519
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_519.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==519)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 519) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_519.csv',  row.names = FALSE)
```

# 523
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_523.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==523)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 523) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_523.csv',  row.names = FALSE)
```

# 532
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_532.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==532)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 532) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_532.csv',  row.names = FALSE)
```

# 548
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_548.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==548)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 548) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_548.csv',  row.names = FALSE)
```

# 555
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_555.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==555)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 555) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_555.csv',  row.names = FALSE)
```

# 563
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_563.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==563)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 563) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_563.csv',  row.names = FALSE)
```

# 580
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_580.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==580)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 580) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_580.csv',  row.names = FALSE)
```

# 589
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_589.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==589)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 589) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_589.csv',  row.names = FALSE)
```

# 605
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_605.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==605)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 605) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_605.csv',  row.names = FALSE)
```

# 610
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_610.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==610)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 610) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_610.csv',  row.names = FALSE)
```

# 644
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_644.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==644)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 644) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_644.csv',  row.names = FALSE)
```

# 653
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_653.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==653)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 653) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_653.csv',  row.names = FALSE)
```

# 657
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_657.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==657)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 657) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_657.csv',  row.names = FALSE)
```

# 661
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_661.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==661)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 661) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_661.csv',  row.names = FALSE)
```

# 666
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_666.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==666)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 666) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_666.csv',  row.names = FALSE)
```

# 674
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_674.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==674)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 674) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_674.csv',  row.names = FALSE)
```

# 688
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_688.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==688)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 688) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_688.csv',  row.names = FALSE)
```

# 695
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_695.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==695)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 695) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_695.csv',  row.names = FALSE)
```

# 713
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_713.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==713)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 713) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_713.csv',  row.names = FALSE)
```

# 729
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_729.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==729)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 729) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_729.csv',  row.names = FALSE)
```

# 772
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_772.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==772)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 772) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_772.csv',  row.names = FALSE)
```


# 816
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_816.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==816)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 816) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_816.csv',  row.names = FALSE)
```


# 825
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_825.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==825)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 825) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_825.csv',  row.names = FALSE)
```


# 828
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_828.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==828)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 828) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_828.csv',  row.names = FALSE)
```

# 835
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_835.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==835)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 835) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_835.csv',  row.names = FALSE)
```

# 843
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_843.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==843)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 843) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_843.csv',  row.names = FALSE)
```


# 847
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_847.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==847)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 847) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_847.csv',  row.names = FALSE)
```

# 863
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_863.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==863)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 863) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_863.csv',  row.names = FALSE)
```


# 864
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_864.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==864)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 864) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_864.csv',  row.names = FALSE)
```

# 890
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_890.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==890)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 890) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_890.csv',  row.names = FALSE)
```

# 903
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_903.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==903)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 903) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_903.csv',  row.names = FALSE)
```

# 906
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_906.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==906)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 906) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_906.csv',  row.names = FALSE)
```

# 936
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_936.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==936)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 936) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_936.csv',  row.names = FALSE)
```

# 981
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_981.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==981)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 981) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_981.csv',  row.names = FALSE)
```

# 982
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_982.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==982)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 982) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_982.csv',  row.names = FALSE)
```

# 988
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_988.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==988)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 988) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_988.csv',  row.names = FALSE)
```


# 990
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_990.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==990)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 990) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_990.csv',  row.names = FALSE)
```

# 1002
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1002.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1002)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1002) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1002.csv',  row.names = FALSE)
```

# 1048
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1048.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1048)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1048) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1048.csv',  row.names = FALSE)
```

# 1075
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1075.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1075)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1075) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1075.csv',  row.names = FALSE)
```

# 1093
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1093.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1093)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1093) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1093.csv',  row.names = FALSE)
```


# 1139
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1139.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1139)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1139) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1139.csv',  row.names = FALSE)
```


# 1150
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1150.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1150)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1150) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1150.csv',  row.names = FALSE)
```



# 1155
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1155.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1155)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1155) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1155.csv',  row.names = FALSE)
```

# 1157
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1157.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1157)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>% 
  mutate(IDobj = 1157) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1157.csv',  row.names = FALSE)
```
# 1168
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1168.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1168)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>% 
  mutate(IDobj = 1168) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1168.csv',  row.names = FALSE)
```

# 1199
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1199.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1199)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1199) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1199.csv',  row.names = FALSE)
```

# 1419
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1419.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1419)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1419) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1419.csv',  row.names = FALSE)
```

# 1545
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1545.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM56.shp", "FiresUTM56")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1545)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>% 
  mutate(IDobj = 1545) %>% 
  mutate(UTMZone = 56) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1545.csv',  row.names = FALSE)
```