---
title: "PatchMetricsByFire2019"
author: "Anna Talucci"
date: "2/13/2022"
output: html_document
---

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

```{r}
firesx = fires %>% filter(FireYr=="2019") 
unique(firesx$IDobj)
```
# Overview

This script process landscape/patch statistics by class burned/unburned **For Each patch** for the 2020 fires in Northeastern Siberia. Fires are processed individually.


[Landscapemetrics package details](https://cran.r-project.org/web/packages/landscapemetrics/landscapemetrics.pdf)



# 154

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_154.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==154)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 154) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_154.csv',  row.names = FALSE)
```


# 163

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_163.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==163)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 163) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_163.csv',  row.names = FALSE)
```

# 167

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_167.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==167)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 167) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_167.csv',  row.names = FALSE)
```


# 171

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_171.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==171)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 171) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_171.csv',  row.names = FALSE)
```

# 174

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_174.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==174)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 174) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_174.csv',  row.names = FALSE)
```

# 178

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_178.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==178)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 178) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_178.csv',  row.names = FALSE)
```


# 180

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_180.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==180)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 180) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_180.csv',  row.names = FALSE)
```


# 182

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_182.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==182)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 182) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_182.csv',  row.names = FALSE)
```

# 187

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_187.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==187)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 187) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_187.csv',  row.names = FALSE)
```

# 194

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_194.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==194)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 194) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_194.csv',  row.names = FALSE)
```

# 199

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_199.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==199)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 199) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_199.csv',  row.names = FALSE)
```

# 204

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_204.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==204)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 204) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_204.csv',  row.names = FALSE)
```


# 207

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_207.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==207)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 207) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_207.csv',  row.names = FALSE)
```

# 211

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_211.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==211)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 211) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_211.csv',  row.names = FALSE)
```

# 214

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_214.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==214)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 214) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_214.csv',  row.names = FALSE)
```


# 221

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_221.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==221)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 221) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_221.csv',  row.names = FALSE)
```


# 226

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_226.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==226)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 226) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_226.csv',  row.names = FALSE)
```

# 227

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_227.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==227)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 227) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_227.csv',  row.names = FALSE)
```


# 229

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_229.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==229)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 229) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_229.csv',  row.names = FALSE)
```

# 233

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_233.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==233)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 233) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_233.csv',  row.names = FALSE)
```

# 237

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_237.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==237)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 237) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_237.csv',  row.names = FALSE)
```

# 243

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_243.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==243)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 243) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_243.csv',  row.names = FALSE)
```

# 249

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_249.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==249)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 249) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_249.csv',  row.names = FALSE)
```

# 253

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_253.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==253)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 253) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_253.csv',  row.names = FALSE)
```

# 256

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_256.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==256)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 256) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_256.csv',  row.names = FALSE)
```


# 257

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_257.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==257)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 257) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_257.csv',  row.names = FALSE)
```

# 258

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_258.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==258)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 258) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_258.csv',  row.names = FALSE)
```

# 265

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_265.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==265)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 265) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_265.csv',  row.names = FALSE)
```

# 277

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_277.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==277)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 277) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_277.csv',  row.names = FALSE)
```

# 281

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_281.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==281)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 281) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_281.csv',  row.names = FALSE)
```

# 289

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_289.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==289)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 289) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_289.csv',  row.names = FALSE)
```

# 297

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_297.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==297)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 297) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_297.csv',  row.names = FALSE)
```

# 300

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_300.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==300)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 300) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_300.csv',  row.names = FALSE)
```

# 304

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_304.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==304)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 304) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_304.csv',  row.names = FALSE)
```

# 307

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_307.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==307)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 307) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_307.csv',  row.names = FALSE)
```

# 312

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_312.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==312)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 312) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_312.csv',  row.names = FALSE)
```

# 318

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_318.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==318)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 318) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_318.csv',  row.names = FALSE)
```

# 319

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_319.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==319)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 319) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_319.csv',  row.names = FALSE)
```

# 321

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_321.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==321)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 321) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_321.csv',  row.names = FALSE)
```

# 326

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_326.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==326)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 326) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_326.csv',  row.names = FALSE)
```

# 327

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_327.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==327)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 327) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_327.csv',  row.names = FALSE)
```

# 328

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_328.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==328)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 328) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_328.csv',  row.names = FALSE)
```

# 334

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_334.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==334)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 334) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_334.csv',  row.names = FALSE)
```

# 337

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_337.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==337)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 337) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_337.csv',  row.names = FALSE)
```

# 339

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_339.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==339)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 339) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_339.csv',  row.names = FALSE)
```

# 341

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_341.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==341)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 341) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_341.csv',  row.names = FALSE)
```

# 343

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_343.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==343)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 343) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_343.csv',  row.names = FALSE)
```

# 347

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_347.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==347)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 347) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_347.csv',  row.names = FALSE)
```

# 358

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_358.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==358)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 358) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_358.csv',  row.names = FALSE)
```

# 362

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_362.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==362)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 362) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_362.csv',  row.names = FALSE)
```

# 370

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_370.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==370)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 370) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_370.csv',  row.names = FALSE)
```

# 371

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_371.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==371)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 371) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_371.csv',  row.names = FALSE)
```

# 374

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_374.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==374)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 374) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_374.csv',  row.names = FALSE)
```

# 379

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_379.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==379)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 379) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_379.csv',  row.names = FALSE)
```

# 381

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_381.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==381)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 381) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_381.csv',  row.names = FALSE)
```

# 384

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_384.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==384)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 384) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_384.csv',  row.names = FALSE)
```

# 393

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_393.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==393)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 393) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_393.csv',  row.names = FALSE)
```

# 402

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_402.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==402)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 402) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_402.csv',  row.names = FALSE)
```

# 412

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_412.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==412)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 412) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_412.csv',  row.names = FALSE)
```

# 421

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_421.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==421)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 421) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_421.csv',  row.names = FALSE)
```

# 423

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_423.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==423)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 423) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_423.csv',  row.names = FALSE)
```

# 433

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_433.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==433)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 433) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_433.csv',  row.names = FALSE)
```


# 439

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_439.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==439)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 439) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_439.csv',  row.names = FALSE)
```

# 444

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_444.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==444)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 444) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_444.csv',  row.names = FALSE)
```

# 446

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_446.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==446)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 446) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_446.csv',  row.names = FALSE)
```

# 453

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_453.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==453)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 453) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_453.csv',  row.names = FALSE)
```

# 463

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_463.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==463)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 463) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_463.csv',  row.names = FALSE)
```


# 468

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_468.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==468)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 468) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_468.csv',  row.names = FALSE)
```

# 470

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_470.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==470)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 470) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_470.csv',  row.names = FALSE)
```

# 496

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_496.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==496)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 496) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_496.csv',  row.names = FALSE)
```


# 498

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_498.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==498)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 498) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_498.csv',  row.names = FALSE)
```

# 500

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_500.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==500)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 500) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_500.csv',  row.names = FALSE)
```

# 509

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_509.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==509)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 509) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_509.csv',  row.names = FALSE)
```

# 512

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_512.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==512)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 512) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_512.csv',  row.names = FALSE)
```

# 514

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_514.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==514)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 514) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_514.csv',  row.names = FALSE)
```

# 518

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_518.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==518)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 518) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_518.csv',  row.names = FALSE)
```

# 521

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_521.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==521)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 521) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_521.csv',  row.names = FALSE)
```


# 525

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_525.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==525)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 525) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_525.csv',  row.names = FALSE)
```

# 531

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_531.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==531)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 531) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_531.csv',  row.names = FALSE)
```

# 533

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_533.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==533)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 533) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_533.csv',  row.names = FALSE)
```

# 535

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_535.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==535)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 535) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_535.csv',  row.names = FALSE)
```


# 540

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_540.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==540)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 540) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_540.csv',  row.names = FALSE)
```

# 545

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_545.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==545)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 545) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_545.csv',  row.names = FALSE)
```

# 555

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_555.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==555)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 555) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_555.csv',  row.names = FALSE)
```

# 556

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_556.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==556)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 556) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_556.csv',  row.names = FALSE)
```

# 557

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_557.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==557)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 557) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_557.csv',  row.names = FALSE)
```

# 573

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_573.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==573)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 573) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_573.csv',  row.names = FALSE)
```

# 578

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_578.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==578)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 578) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_578.csv',  row.names = FALSE)
```

# 602

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_602.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==602)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 602) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_602.csv',  row.names = FALSE)
```

# 607

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_607.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==607)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 607) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_607.csv',  row.names = FALSE)
```

# 608

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_608.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==608)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 608) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_608.csv',  row.names = FALSE)
```

# 618

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_618.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==618)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 618) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_618.csv',  row.names = FALSE)
```

# 621

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_621.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==620)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 620) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_620.csv',  row.names = FALSE)
```

# 621

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_621.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==621)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 621) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_621.csv',  row.names = FALSE)
```

# 629

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_629.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==629)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 629) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_629.csv',  row.names = FALSE)
```

# 633

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_633.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==633)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 633) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_633.csv',  row.names = FALSE)
```

# 638

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_638.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==638)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 638) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_638.csv',  row.names = FALSE)
```

# 641

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_641.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==641)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 641) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_641.csv',  row.names = FALSE)
```

# 643

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_643.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==643)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 643) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_643.csv',  row.names = FALSE)
```

# 647

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_647.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==647)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 647) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_647.csv',  row.names = FALSE)
```

# 650

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_650.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==650)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 650) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_650.csv',  row.names = FALSE)
```

# 652

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_652.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==652)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 652) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_652.csv',  row.names = FALSE)
```

# 662

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_662.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==662)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 662) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_662.csv',  row.names = FALSE)
```

# 665

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_665.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==665)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 665) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_665.csv',  row.names = FALSE)
```

# 674

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_674.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==674)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 674) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_674.csv',  row.names = FALSE)
```

# 682

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_682.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==682)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 682) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_682.csv',  row.names = FALSE)
```

# 683

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_683.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==683)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 683) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_683.csv',  row.names = FALSE)
```

# 686

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_686.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==686)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 686) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_686.csv',  row.names = FALSE)
```

# 687

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_687.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==687)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 687) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_687.csv',  row.names = FALSE)
```

# 692

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_692.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==692)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 692) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_692.csv',  row.names = FALSE)
```

# 694

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_694.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==694)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 694) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_694.csv',  row.names = FALSE)
```

# 697

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_697.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==697)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 697) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_697.csv',  row.names = FALSE)
```

# 701

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_701.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==701)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 701) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_701.csv',  row.names = FALSE)
```

# 703

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_703.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==703)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 703) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_703.csv',  row.names = FALSE)
```

# 721

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_721.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==721)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 721) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_721.csv',  row.names = FALSE)
```

# 735

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_735.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==735)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 735) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_735.csv',  row.names = FALSE)
```

# 743

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_743.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==743)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 743) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_743.csv',  row.names = FALSE)
```

# 744

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_744.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==744)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 744) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_744.csv',  row.names = FALSE)
```

# 749

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_749.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==749)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 749) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_749.csv',  row.names = FALSE)
```

# 755

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_755.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==755)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 755) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_755.csv',  row.names = FALSE)
```

# 760

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_760.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==760)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 760) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_760.csv',  row.names = FALSE)
```

# 766

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_766.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==766)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 766) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_766.csv',  row.names = FALSE)
```

# 774

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_774.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==774)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 774) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_774.csv',  row.names = FALSE)
```

# 781

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_781tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==781)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 781) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_781.csv',  row.names = FALSE)
```

# 788

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_788tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==788)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 788) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_788.csv',  row.names = FALSE)
```

# 789

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_789tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==789)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 789) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_789.csv',  row.names = FALSE)
```

# 800

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_800tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==800)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 800) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_800.csv',  row.names = FALSE)
```

# 801

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_801tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==801)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 801) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_801.csv',  row.names = FALSE)
```

# 806

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_806tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==806)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 806) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_806.csv',  row.names = FALSE)
```

# 807

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_807tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==807)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 807) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_807.csv',  row.names = FALSE)
```

# 808

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_808tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==808)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 808) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_808.csv',  row.names = FALSE)
```

# 812

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_812tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==812)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 812) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_812.csv',  row.names = FALSE)
```

# 814

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_814tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==814)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 814) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_814.csv',  row.names = FALSE)
```

# 834

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_834tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==834)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 834) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_834.csv',  row.names = FALSE)
```

# 844

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_844tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==844)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 844) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_844.csv',  row.names = FALSE)
```

# 854

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_854tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==854)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 854) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_854.csv',  row.names = FALSE)
```

# 855

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_855tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==855)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 855) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_855.csv',  row.names = FALSE)
```

# 906

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_906tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==906)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 906) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_906.csv',  row.names = FALSE)
```

# 908

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_908tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==908)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 908) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_908.csv',  row.names = FALSE)
```

# 919

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_919tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==919)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 919) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_919.csv',  row.names = FALSE)
```

# 924

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_924tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==924)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 924) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_924.csv',  row.names = FALSE)
```

# 929

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_929tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==929)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 929) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_929.csv',  row.names = FALSE)
```


# 943

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_943tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==943)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 943) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_943.csv',  row.names = FALSE)
```

# 969

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_969tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==969)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 969) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_969.csv',  row.names = FALSE)
```

# 979

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_979tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==979)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 979) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_979.csv',  row.names = FALSE)
```

# 986

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_986tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==986)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 986) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_986.csv',  row.names = FALSE)
```

# 999

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_999tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==999)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 999) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_999.csv',  row.names = FALSE)
```

# 1000

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1000tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1000)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1000) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1000.csv',  row.names = FALSE)
```

# 1016

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1016tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1016)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1016) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1016.csv',  row.names = FALSE)
```

# 1018

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1018tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1018)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1018) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1018.csv',  row.names = FALSE)
```

# 1019

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1019tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1019)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1019) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1019.csv',  row.names = FALSE)
```

# 1025

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1025tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1025)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1025) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1025.csv',  row.names = FALSE)
```

# 1033

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1033tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1033)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1033) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1033.csv',  row.names = FALSE)
```

# 1044

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1044tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1044)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1044) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1044.csv',  row.names = FALSE)
```

# 1047

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1047tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1047)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1047) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1047.csv',  row.names = FALSE)
```

# 1050

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1050tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1050)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1050) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1050.csv',  row.names = FALSE)
```

# 1052

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1052tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1052)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1052) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1052.csv',  row.names = FALSE)
```

# 1054

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1054tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1054)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1054) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1054.csv',  row.names = FALSE)
```

# 1095

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1095tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1095)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1095) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1095.csv',  row.names = FALSE)
```

# 1104

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1104tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1104)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1104) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1104.csv',  row.names = FALSE)
```

# 1112

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1112tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1112)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1112) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1112.csv',  row.names = FALSE)
```

# 1113

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1113tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1113)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1113) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1113.csv',  row.names = FALSE)
```

# 1120

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1120tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1120)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1120) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1120.csv',  row.names = FALSE)
```

# 1128

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1128tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1128)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1128) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1128.csv',  row.names = FALSE)
```

# 1130

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1130tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1130)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1130) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1130.csv',  row.names = FALSE)
```

# 1153

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1153tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1153)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1153) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1153.csv',  row.names = FALSE)
```

# 1157

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1157tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1157)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1157) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1157.csv',  row.names = FALSE)
```

# 1161

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1161tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1161)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1161) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1161.csv',  row.names = FALSE)
```

# 1163

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1163tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1163)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1163) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1163.csv',  row.names = FALSE)
```

# 1170

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1170tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1170)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1170) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1170.csv',  row.names = FALSE)
```

# 1179

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1179tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1179)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 179) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1179.csv',  row.names = FALSE)
```

# 1181

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1181tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1181)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1181) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1181.csv',  row.names = FALSE)
```

# 1186

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1186tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1186)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1186) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1186.csv',  row.names = FALSE)
```

# 1200

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1200tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1200)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1200) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1200.csv',  row.names = FALSE)
```

# 1206

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1206tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1206)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1206) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1206.csv',  row.names = FALSE)
```

# 1211

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1211tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1211)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1211) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1211.csv',  row.names = FALSE)
```

# 1230

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1230tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1230)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1230) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1230.csv',  row.names = FALSE)
```

# 1236

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1236tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1236)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1236) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1236.csv',  row.names = FALSE)
```

# 1245

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1245tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1245)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1245) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1245.csv',  row.names = FALSE)
```

# 1266

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2019Binary/2019BinaryImg_1266tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2019") %>%
  filter(IDobj==1266)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1266) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2019patchFire_1266.csv',  row.names = FALSE)
```

