---
title: "Patch Metric by Fire UTM 51"
author: "Anna Talucci"
date: "1/31/2022"
output: html_document
---
# Overview

This script process landscape/patch statistics by class burned/unburned **For Each patch** for the 2020 fires in Northeastern Siberia. Fires are processed individually.


[Landscapemetrics package details](https://cran.r-project.org/web/packages/landscapemetrics/landscapemetrics.pdf)

For UTM zone 51 fires

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_4049.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM51.shp", "FiresUTM51")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==4049)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r eval=FALSE, include=FALSE}
landscape %>% 
  calculate_lsm(., level = "patch", full_name = TRUE) %>% 
  mutate(IDobj = 4049) %>% 
  mutate(UTMZone = 51) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_4049-1.csv',  row.names = FALSE)
```

 what = c("patch", "lsm_c_te", "lsm_l_pr"))
```{r eval=FALSE, include=FALSE}
landscape %>% 
  calculate_lsm(.,  what = c("patch", "lsm_p_area", "lsm_p_core")) %>% 
  mutate(IDobj = 4049) %>% 
  mutate(UTMZone = 51) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_4049-2.csv',  row.names = FALSE)
```

```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>% 
  mutate(IDobj = 4049) %>% 
  mutate(UTMZone = 51) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_4049.csv',  row.names = FALSE)
```