---
title: "PatchMetric By fire 2015"
author: "Anna Talucci"
date: "2/20/2022"
output: html_document
---




# Overview

This script process landscape/patch statistics by class burned/unburned **For Each patch** for the 2020 fires in Northeastern Siberia. Fires are processed individually.


[Landscapemetrics package details](https://cran.r-project.org/web/packages/landscapemetrics/landscapemetrics.pdf)



# 61

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_61.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==61)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 61) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_61.csv',  row.names = FALSE)
```


# 72

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_72.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==72)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 72) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_72.csv',  row.names = FALSE)
```

# 77

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_77.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==77)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 77) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_77.csv',  row.names = FALSE)
```


# 93

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_93.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==93)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 93) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_93.csv',  row.names = FALSE)
```

# 110

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_110.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==110)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 110) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_110.csv',  row.names = FALSE)
```

# 134

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_134.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==134)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 134) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_134.csv',  row.names = FALSE)
```


# 148

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_148.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==148)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 148) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_148.csv',  row.names = FALSE)
```


# 152

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_152.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==152)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 152) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_152.csv',  row.names = FALSE)
```

# 164

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_164.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==164)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 164) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_164.csv',  row.names = FALSE)
```

# 198

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_198.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==198)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 198) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_198.csv',  row.names = FALSE)
```

# 220

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_220.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==220)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 220) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_220.csv',  row.names = FALSE)
```

# 224

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_224.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==224)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 224) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_224.csv',  row.names = FALSE)
```


# 229

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_229.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==229)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 229) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_229.csv',  row.names = FALSE)
```

# 240

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_240.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==240)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 240) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_240.csv',  row.names = FALSE)
```

# 241

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_241.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==241)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 241) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_241.csv',  row.names = FALSE)
```


# 258

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_258.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==258)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 258) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_258.csv',  row.names = FALSE)
```


# 271

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_271.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==271)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 271) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_271.csv',  row.names = FALSE)
```

#273

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_273.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==273)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj =273) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_273.csv',  row.names = FALSE)
```


# 276

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_276.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==276)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 276) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_276.csv',  row.names = FALSE)
```

# 282

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_282.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==282)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 282) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_282.csv',  row.names = FALSE)
```

# 300

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_300.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==300)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 300) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_300.csv',  row.names = FALSE)
```

# 302

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_302.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==302)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 302) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_302.csv',  row.names = FALSE)
```

# 312

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_312.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==312)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 312) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_312.csv',  row.names = FALSE)
```

# 315

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_315.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==315)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 315) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_315.csv',  row.names = FALSE)
```

# 324

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_324.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==324)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 324) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_324.csv',  row.names = FALSE)
```


# 338

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_338.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==338)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 338) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_338.csv',  row.names = FALSE)
```

# 396

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_396.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==396)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 396) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_396.csv',  row.names = FALSE)
```

# 490

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_490.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==490)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 490) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_490.csv',  row.names = FALSE)
```

# 631

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_631.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==631)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 631) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_631.csv',  row.names = FALSE)
```

# 768

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_768.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==768)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 768) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_768.csv',  row.names = FALSE)
```

# 774

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_774.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==774)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 774) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_774.csv',  row.names = FALSE)
```

# 881

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_881.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==881)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 881) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_881.csv',  row.names = FALSE)
```

# 1213

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1213.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1213)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1213) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1213.csv',  row.names = FALSE)
```

# 1219

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1219.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1219)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1219) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1219.csv',  row.names = FALSE)
```

# 1239

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1239.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1239)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1239) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1239.csv',  row.names = FALSE)
```

# 1258

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1258.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1258)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1258) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1258.csv',  row.names = FALSE)
```

# 1260

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1260.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1260)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1260) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1260.csv',  row.names = FALSE)
```

# 1318

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1318.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1318)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1318) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1318.csv',  row.names = FALSE)
```

# 1331

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1331.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1331)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1331) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1331.csv',  row.names = FALSE)
```

# 1475

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1475.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1475)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1475) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1475.csv',  row.names = FALSE)
```

# 1502

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1502.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1502)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1502) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1502.csv',  row.names = FALSE)
```

# 1596

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1596.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1596)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1596) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1596.csv',  row.names = FALSE)
```

# 1933

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1933.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1933)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1933) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1933.csv',  row.names = FALSE)
```

# 1938

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_1938.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==1938)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1938) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_1938.csv',  row.names = FALSE)
```

# 2102

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_2102.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==2102)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2102) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_2102.csv',  row.names = FALSE)
```

# 2150

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_2150.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==2150)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2150) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_2150.csv',  row.names = FALSE)
```

# 2320

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_2320.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==2320)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2320) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_2320.csv',  row.names = FALSE)
```

# 2542

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2015Binary/2015BinaryImg_2542.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2015") %>%
  filter(IDobj==2542)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2542) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2015patchFire_2542.csv',  row.names = FALSE)
```
