---
title: "Patch Metrics by Fire 2018"
author: "Anna Talucci"
date: "2/15/2022"
output: html_document
---



# Overview

This script process landscape/patch statistics by class burned/unburned **For Each patch** for the 2020 fires in Northeastern Siberia. Fires are processed individually.


[Landscapemetrics package details](https://cran.r-project.org/web/packages/landscapemetrics/landscapemetrics.pdf)



# 39

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_39.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==39)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 39) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_39.csv',  row.names = FALSE)
```


# 46

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_46.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==46)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 46) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_46.csv',  row.names = FALSE)
```

# 47

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_47.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==47)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 47) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_47.csv',  row.names = FALSE)
```


# 48

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_48.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==48)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 48) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_48.csv',  row.names = FALSE)
```

# 53

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_53.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==53)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 53) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_53.csv',  row.names = FALSE)
```

# 55

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_55.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==55)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 55) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_55.csv',  row.names = FALSE)
```


# 59

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_59.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==59)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 59) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_59.csv',  row.names = FALSE)
```


# 63

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_63.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==63)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 63) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_63.csv',  row.names = FALSE)
```

# 64

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_64.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==64)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 64) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_64.csv',  row.names = FALSE)
```

# 65

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_65.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==65)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 65) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_65.csv',  row.names = FALSE)
```

# 71

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_71.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==71)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 71) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_71.csv',  row.names = FALSE)
```

# 74

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_74.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==74)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 74) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_74.csv',  row.names = FALSE)
```


# 77

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_77.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==77)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 77) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_77.csv',  row.names = FALSE)
```

# 87

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_87.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==87)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 87) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_87.csv',  row.names = FALSE)
```

# 90

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_90.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==90)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 90) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_90.csv',  row.names = FALSE)
```


# 93

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_93.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==93)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 93) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_93.csv',  row.names = FALSE)
```


# 96

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_96.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==96)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 96) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_96.csv',  row.names = FALSE)
```

# 102

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_102.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==102)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 102) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_102.csv',  row.names = FALSE)
```


# 111

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_111.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==111)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 111) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_111.csv',  row.names = FALSE)
```

# 118

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_118.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==118)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 118) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_118.csv',  row.names = FALSE)
```

# 123

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_123.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==123)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 123) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_123.csv',  row.names = FALSE)
```

# 129

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_129.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==129)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 129) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_129.csv',  row.names = FALSE)
```

# 132

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_132.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==132)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 132) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_132.csv',  row.names = FALSE)
```

# 139

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_139.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==139)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 139) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_139.csv',  row.names = FALSE)
```

# 141

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_141.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==141)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 141) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_141.csv',  row.names = FALSE)
```


# 142

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_142.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==142)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 142) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_142.csv',  row.names = FALSE)
```

# 165

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_165.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==165)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 165) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_165.csv',  row.names = FALSE)
```

# 167

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_167.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==167)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 167) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_167.csv',  row.names = FALSE)
```

# 183

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_183.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==183)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 183) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_183.csv',  row.names = FALSE)
```

# 209

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_209.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==209)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 209) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_209.csv',  row.names = FALSE)
```

# 230

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_230.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==230)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 230) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_230.csv',  row.names = FALSE)
```

# 242

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_242.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==242)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 242) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_242.csv',  row.names = FALSE)
```

# 246

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_246.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==246)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 246) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_246.csv',  row.names = FALSE)
```

# 251

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_251.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==251)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 251) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_251.csv',  row.names = FALSE)
```

# 253

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_253.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==253)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 253) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_253.csv',  row.names = FALSE)
```

# 255

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_255.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==255)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 255) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_255.csv',  row.names = FALSE)
```

# 258

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_258.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==258)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 258) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_258.csv',  row.names = FALSE)
```

# 259

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_259.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==259)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 259) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_259.csv',  row.names = FALSE)
```

# 277

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_277.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==277)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 277) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_277.csv',  row.names = FALSE)
```

# 288

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_288.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==288)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 288) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_288.csv',  row.names = FALSE)
```

# 299

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_299.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==299)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 299) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_299.csv',  row.names = FALSE)
```

# 305

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_305.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==305)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 305) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_305.csv',  row.names = FALSE)
```

# 310

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_310.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==310)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 310) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_310.csv',  row.names = FALSE)
```

# 312

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_312.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==312)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 312) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_312.csv',  row.names = FALSE)
```

# 313

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_313.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==313)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 313) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_313.csv',  row.names = FALSE)
```

# 336

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_336.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==336)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 336) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_336.csv',  row.names = FALSE)
```

# 367

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_367.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==367)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 367) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_367.csv',  row.names = FALSE)
```

# 476

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_476.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==476)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 476) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_476.csv',  row.names = FALSE)
```

# 478

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_478.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==478)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 478) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_478.csv',  row.names = FALSE)
```

# 517

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_517.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==517)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 517) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_517.csv',  row.names = FALSE)
```

# 384

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_384.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==384)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 384) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_384.csv',  row.names = FALSE)
```

# 416

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_416.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==416)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 416) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_416.csv',  row.names = FALSE)
```

# 436

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_436.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==436)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 436) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_436.csv',  row.names = FALSE)
```

# 476

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_476.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==476)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 476) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_476.csv',  row.names = FALSE)
```

# 478

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_478.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==478)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 478) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_478.csv',  row.names = FALSE)
```

# 517

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_517.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==517)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 517) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_517.csv',  row.names = FALSE)
```

# 552

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_552.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==552)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 552) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_552.csv',  row.names = FALSE)
```

# 742

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_742.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==742)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 742) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_742.csv',  row.names = FALSE)
```

# 755

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_755.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==755)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 755) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_755.csv',  row.names = FALSE)
```

# 760

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_760.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==760)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 760) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_760.csv',  row.names = FALSE)
```

# 774

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_774.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==774)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 774) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_774.csv',  row.names = FALSE)
```

# 837

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_837.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==837)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 837) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_837.csv',  row.names = FALSE)
```


# 897

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_897.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==897)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 897) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_897.csv',  row.names = FALSE)
```

# 971

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_971.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==971)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 971) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_971.csv',  row.names = FALSE)
```

# 1040

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1040.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1040)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1040) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1040.csv',  row.names = FALSE)
```

# 1099

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1099.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1099)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1099) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1099.csv',  row.names = FALSE)
```

# 1208

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1208.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1208)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1208) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1208.csv',  row.names = FALSE)
```


# 1246

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1246.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1246)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1246) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1246.csv',  row.names = FALSE)
```

# 1257

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1257.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1257)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1257) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1257.csv',  row.names = FALSE)
```

# 1259

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1259.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1259)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1259) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1259.csv',  row.names = FALSE)
```


# 1272

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1272.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1272)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1272) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1272.csv',  row.names = FALSE)
```

# 1279

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1279.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1279)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1279) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1279.csv',  row.names = FALSE)
```

# 1282

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1282.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1282)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1282) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1282.csv',  row.names = FALSE)
```

# 1289

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1289.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1289)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1289) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1289.csv',  row.names = FALSE)
```

# 1296

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1296.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1296)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1296) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1296.csv',  row.names = FALSE)
```

# 1317

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1317.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1317)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1317) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1317.csv',  row.names = FALSE)
```

# 1430

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1430.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1430)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1430) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1430.csv',  row.names = FALSE)
```


# 1485

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1485.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1485)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1485) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1485.csv',  row.names = FALSE)
```

# 1492

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1492.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1492)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1492) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1492.csv',  row.names = FALSE)
```

# 1530

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1530.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1530)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1530) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1530.csv',  row.names = FALSE)
```

# 1552

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1552.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1552)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1552) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1552.csv',  row.names = FALSE)
```


# 1589

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1589.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1589)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1589) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1589.csv',  row.names = FALSE)
```

# 1652

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1652.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1652)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1652) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1652.csv',  row.names = FALSE)
```

# 1668

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1668.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1668)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1668) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1668.csv',  row.names = FALSE)
```

# 1684

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1684.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1684)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1684) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1684.csv',  row.names = FALSE)
```

# 1690

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1690.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1690)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1690) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1690.csv',  row.names = FALSE)
```

# 1695

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1695.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1695)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1695) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1695.csv',  row.names = FALSE)
```

# 1710

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1710.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1710)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1710) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1710.csv',  row.names = FALSE)
```

# 1720

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1720.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1720)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1720) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1720.csv',  row.names = FALSE)
```

# 1741

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1741.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1741)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1741) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1741.csv',  row.names = FALSE)
```

# 1784

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1784.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1784)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1784) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1784.csv',  row.names = FALSE)
```

# 1805

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1805.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1805)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1805) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1805.csv',  row.names = FALSE)
```

# 1831

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_1831.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==1831)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1831) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_1831.csv',  row.names = FALSE)
```

# 2032

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2032.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2032)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2032) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2032.csv',  row.names = FALSE)
```

# 2047

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2047.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2047)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2047) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2047.csv',  row.names = FALSE)
```

# 2111

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2111.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2111)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2111) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2111.csv',  row.names = FALSE)
```

# 2149

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2149.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2149)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2149) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2149.csv',  row.names = FALSE)
```

# 2436

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2436.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2436)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2436) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2436.csv',  row.names = FALSE)
```

# 2451

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2451.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2451)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2451) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2451.csv',  row.names = FALSE)
```

# 2477

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2477.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2477)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2477) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2477.csv',  row.names = FALSE)
```

# 2496

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2496.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2496)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2496) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2496.csv',  row.names = FALSE)
```

# 2497

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2497.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2497)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2497) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2497.csv',  row.names = FALSE)
```

# 2545

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2545.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2545)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2545) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2545.csv',  row.names = FALSE)
```

# 2663

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2663.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2663)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2663) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2663.csv',  row.names = FALSE)
```

# 2700

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2700.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2700)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2700) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2700.csv',  row.names = FALSE)
```

# 2759

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2759.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2759)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2759) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2759.csv',  row.names = FALSE)
```

# 2860

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2860.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2860)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2860) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2860.csv',  row.names = FALSE)
```

# 2864

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_2864.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==2864)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2864) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_2864.csv',  row.names = FALSE)
```

# 3003

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_3003.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==3003)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 3003) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_3003.csv',  row.names = FALSE)
```

# 3090

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_3090.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==3090)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 3090) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_3090.csv',  row.names = FALSE)
```

# 3153

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2018Binary/2018BinaryImg_3153.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2018") %>%
  filter(IDobj==3153)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 3153) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2018patchFire_3153.csv',  row.names = FALSE)
```


