---
title: "Patch Summaries For Paper"
author: "Anna Talucci"
date: "11/3/2021"
output: html_document
---

# Clear workspace

```{r}
rm(list=ls()) 
```

# Overview

# Fires with Scanline Errors
```{r}
target = c(351, 361, 403, 422, 428, 434, 439, 498, 544, 550, 598, 636, 808, 892, 944, 1097, 1190, 1275, 1363, 1416, 1742, 1773, 2135, 2216, 2295,2322, 2346, 2350, 2351, 2358, 2367, 2383, 2466, 2491, 2514, 2722, 2757, 2833, 2905, 3008, 3213)
```

# Packages

```{r}
library(tidyverse)
```

# Define graph Theme and color Palette 

##Themes
```{r}
lb_theme = theme_bw() + theme(legend.position = "bottom") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```

```{r}
bar_theme = theme_bw() + 
  theme(legend.position = "none", legend.title = element_blank()) +
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black")) 
```

```{r}
ecoPalette <- c("#b5b35c", "#556b2f")
```


# Data

## Fire data

```{r}
fires = read.csv("../data/NESiberiaFires/NESiberiaFires2020.csv") 
```

## Class patch summaries


```{r}
csv_patch = list.files(path = '../data/PatchSummaryUTM', pattern = "csv$", full.names = TRUE)
```

```{r include=FALSE}
stacked_patch <- map_dfr(csv_patch, read_csv)
```

# Organize Patch Class Data 
1. Filter - remove fires with scanline error
2. Pivot Wider so each patch metric is a column
```{r}
df1 = stacked_patch %>% 
  filter(!IDobj %in% target) %>%
  pivot_wider(id_cols =  c(IDobj, class), names_from = metric, values_from = value)

```

```{r eval=FALSE, include=FALSE}
unique(df1$IDobj)
```


# Combine Fire data with Patch data

```{r}
data1 = merge(df1, fires, by = "IDobj")
```

```{r}
data1
```

```{r}
data2 = data1 %>% 
  mutate(LogHa = log(SizeHa))  %>%
  mutate(Logarea_mn = log(area_mn))  %>%
  dplyr::select(IDobj:class, area_mn, ca,np, enn_mn, para_mn, pd, pland, tca, SizeHa, EcoCode, ArcSub, SizeCl, LogHa, Logarea_mn) 
  
data2
```

```{r}
refugia = data2 %>% 
  filter(class==1) %>%
  mutate(Logca = log(ca))  %>%
  mutate(Logtca = log(tca)) %>%
  mutate(FireSize = ifelse((SizeCl %in% 1:3), "small", 
                      ifelse((SizeCl %in% 4:6), "moderate", "large"))) 

refugia
```
Write refugia data to file


```{r}
burnt = data2 %>% 
  filter(class==0) %>%
  mutate(Logca = log(ca))  

burnt
```

# Summaries patch data

Data of interest
- Mean of patch area (Area and edge metric)
- Perimeter-area ratio lsm_c_para_cv
- Percentage of landscape
- Total Core Area

Class
- 0 Burned
- 1 Unburned

```{r}
refugia %>% 
  group_by(EcoCode, ArcSub) %>%
  summarise(mean = mean(area_mn),
            sd = sd(area_mn),
            n = n(),
            se = sd / sqrt(n))


```

```{r}
refugia %>% 
  group_by(EcoCode, ArcSub) %>%
  summarise(mean = mean(pd),
            sd = sd(pd),
            n = n(),
            se = sd / sqrt(n))


```

```{r}
target_patch = c(601, 673, 872, 885, 1166, 1327)
```

```{r}

data2 %>% 
  filter(IDobj %in% target_patch) %>%
   mutate(mean_tca_patch = tca/np) %>%
  mutate(radiusTca = sqrt(((mean_tca_patch*10000)/3.14))) %>%
  dplyr::select(IDobj:area_mn, enn_mn, tca, mean_tca_patch, radiusTca, np, SizeHa:SizeCl) 
```

```{r}
data1 %>%
  dplyr::select(IDobj:class, EcoCode, ArcSub, core_mn, ) %>%
  mutate(rad_core = sqrt(((core_mn*10000)/3.14))) %>%
  group_by(class, EcoCode, ArcSub) %>%
  summarise(mean = mean(rad_core),
            min = min(rad_core),
            max = max(rad_core),
            sd = sd(rad_core),
            n = n(),
            se = sd / sqrt(n))



```

```{r}
data1 %>%
  filter(IDobj %in% target_patch) %>%
  dplyr::select(IDobj:class, EcoCode, ArcSub, core_mn, ) %>%
  mutate(rad_core = sqrt(((core_mn*10000)/3.14))) %>%
  group_by(class, IDobj) 



```