---
title: "Patch Metric by Fire UTM 58"
author: "Anna Talucci"
date: "1/30/2022"
output: html_document
---

# Overview

This script process landscape/patch statistics by class burned/unburned **For Each patch** for the 2020 fires in Northeastern Siberia. Fires are processed individually.


[Landscapemetrics package details](https://cran.r-project.org/web/packages/landscapemetrics/landscapemetrics.pdf)

For UTM zone 58 fire


# 396
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_396.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==396)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 396) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_396.csv',  row.names = FALSE)
```

# 407
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_407.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==407)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 407) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_407.csv',  row.names = FALSE)
```

# 481
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_481.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==481)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 481) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_481.csv',  row.names = FALSE)
```

# 504
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_504.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==504)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 504) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_504.csv',  row.names = FALSE)
```

# 507
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_507.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==507)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 507) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_507.csv',  row.names = FALSE)
```

# 510
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_510.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==510)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 510) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_510.csv',  row.names = FALSE)
```

# 526
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_526.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==526)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 526) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_526.csv',  row.names = FALSE)
```

# 587
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_587.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==587)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 587) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_587.csv',  row.names = FALSE)
```

# 591
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_591.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==591)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 591) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_591.csv',  row.names = FALSE)
```

# 594
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_594.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==594)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 594) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_594.csv',  row.names = FALSE)
```

# 603
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_603.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==603)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 603) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_603.csv',  row.names = FALSE)
```

# 604
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_604.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==604)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 604) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_604.csv',  row.names = FALSE)
```

# 608
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_608.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==608)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 608) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_608.csv',  row.names = FALSE)
```

# 624
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_624.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==624)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 624) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_624.csv',  row.names = FALSE)
```

# 625
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_625.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==625)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 625) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_625.csv',  row.names = FALSE)
```

# 645
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_645.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==645)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 645) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_645.csv',  row.names = FALSE)
```

# 668
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_668.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==668)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 668) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_668.csv',  row.names = FALSE)
```

# 690
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_690.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==690)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 690) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_690.csv',  row.names = FALSE)
```

# 692
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_692.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==692)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 692) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_692.csv',  row.names = FALSE)
```

# 710
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_710.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==710)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 710) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_710.csv',  row.names = FALSE)
```

# 736
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_736.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==736)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 736) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_736.csv',  row.names = FALSE)
```

# 740
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_740.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==740)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 740) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_740.csv',  row.names = FALSE)
```

# 761
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_761.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==761)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 761) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_761.csv',  row.names = FALSE)
```

# 765
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_765.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==765)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 765) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_765.csv',  row.names = FALSE)
```

# 779
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_779.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==779)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 779) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_779.csv',  row.names = FALSE)
```


# 800
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_800.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==800)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 800) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_800.csv',  row.names = FALSE)
```


# 820
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_820.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==820)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 820) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_820.csv',  row.names = FALSE)
```



# 840
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_840.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==840)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 840) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_840.csv',  row.names = FALSE)
```

# 877
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_877.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==877)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>% 
  mutate(IDobj = 877) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_877.csv',  row.names = FALSE)
```
# 880
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_880.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==880)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>% 
  mutate(IDobj = 880) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_880.csv',  row.names = FALSE)
```

# 885
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_885.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==885)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 885) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_885.csv',  row.names = FALSE)
```

# 922
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_922.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==922)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 922) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_922.csv',  row.names = FALSE)
```

# 976
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_976.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM58.shp", "FiresUTM58")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==976)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>% 
  mutate(IDobj = 976) %>% 
  mutate(UTMZone = 58) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_976.csv',  row.names = FALSE)
```