---
title: "PatchMetrics by Fire 2014"
author: "Anna Talucci"
date: "2/25/2022"
output: html_document
---





# Overview

This script process landscape/patch statistics by class burned/unburned **For Each patch** for the 2020 fires in Northeastern Siberia. Fires are processed individually.


[Landscapemetrics package details](https://cran.r-project.org/web/packages/landscapemetrics/landscapemetrics.pdf)



# 17

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_17.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==17)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 17) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_17.csv',  row.names = FALSE)
```


# 18

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_18.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==18)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 18) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_18.csv',  row.names = FALSE)
```

# 19

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_19.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==19)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 19) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_19.csv',  row.names = FALSE)
```


# 21

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_21.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==21)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 21) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_21.csv',  row.names = FALSE)
```

# 22

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_22.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==22)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 22) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_22.csv',  row.names = FALSE)
```

# 28

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_28.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==28)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 28) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_28.csv',  row.names = FALSE)
```


# 32

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_32.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==32)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 32) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_32.csv',  row.names = FALSE)
```


# 154

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_154.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==154)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 154) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_154.csv',  row.names = FALSE)
```

# 210

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_210.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==210)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 210) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_210.csv',  row.names = FALSE)
```

# 227

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_227.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==227)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 227) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_227.csv',  row.names = FALSE)
```

# 256

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_256.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==256)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 256) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_256.csv',  row.names = FALSE)
```

# 352

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_352.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==352)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 352) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_352.csv',  row.names = FALSE)
```


# 359

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_359.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==359)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 359) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_359.csv',  row.names = FALSE)
```

# 388

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_388.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==388)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 388) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_388.csv',  row.names = FALSE)
```

# 405

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_405.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==405)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 405) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_405.csv',  row.names = FALSE)
```


# 446

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_446.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==446)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 446) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_446.csv',  row.names = FALSE)
```


# 618

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_618.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==618)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 618) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_618.csv',  row.names = FALSE)
```

#690

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_690.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==690)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj =690) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_690.csv',  row.names = FALSE)
```


# 725

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_725.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==725)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 725) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_725.csv',  row.names = FALSE)
```

# 769

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_769.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==769)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 769) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_769.csv',  row.names = FALSE)
```

# 795

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_795.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==795)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 795) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_795.csv',  row.names = FALSE)
```

# 812

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_812.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==812)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 812) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_812.csv',  row.names = FALSE)
```

# 829

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_829.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==829)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 829) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_829.csv',  row.names = FALSE)
```

# 830

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_830.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==830)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 830) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_830.csv',  row.names = FALSE)
```

# 841

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_841.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==841)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 841) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_841.csv',  row.names = FALSE)
```


# 879

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_879.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==879)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 879) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_879.csv',  row.names = FALSE)
```

# 932

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_932.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==932)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 932) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_932.csv',  row.names = FALSE)
```

# 975

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_975.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==975)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 975) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_975.csv',  row.names = FALSE)
```

# 986

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_986.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==986)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 986) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_986.csv',  row.names = FALSE)
```

# 992

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_992.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==992)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 992) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_992.csv',  row.names = FALSE)
```

# 1001

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1001.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1001)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1001) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1001.csv',  row.names = FALSE)
```

# 1013

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1013.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1013)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1013) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1013.csv',  row.names = FALSE)
```

# 1073

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1073.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1073)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1073) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1073.csv',  row.names = FALSE)
```

# 1081

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1081.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1081)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1081) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1081.csv',  row.names = FALSE)
```

# 1087

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1087.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1087)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1087) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1087.csv',  row.names = FALSE)
```

# 1090

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1090.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1090)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1090) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1090.csv',  row.names = FALSE)
```

# 1094

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1094.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1094)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1094) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1094.csv',  row.names = FALSE)
```

# 1248

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1248.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1248)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1248) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1248.csv',  row.names = FALSE)
```

# 1289

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1289.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1289)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1289) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1289.csv',  row.names = FALSE)
```

# 1470

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1470.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1470)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1470) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1470.csv',  row.names = FALSE)
```

# 1492

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1492.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1492)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1492) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1492.csv',  row.names = FALSE)
```

# 1493

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1493.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1493)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1493) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1493.csv',  row.names = FALSE)
```

# 1496

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1496.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1496)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1496) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1496.csv',  row.names = FALSE)
```

# 1552

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1552.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1552)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1552) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1552.csv',  row.names = FALSE)
```

# 1601

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1601.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1601)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1601) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1601.csv',  row.names = FALSE)
```

# 1630

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1630.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1630)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1630) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1630.csv',  row.names = FALSE)
```

# 1652

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1652.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1652)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1652) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1652.csv',  row.names = FALSE)
```

# 1691

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_1691.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==1691)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1691) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_1691.csv',  row.names = FALSE)
```

# 5555

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_5555.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==5555)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 5555) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_5555.csv',  row.names = FALSE)
```

# 5555

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2014Binary/2014BinaryImg_5555.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2014") %>%
  filter(IDobj==5555)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 5555) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2014patchFire_5555.csv',  row.names = FALSE)
```
