---
title: "Patch Metrics By Fire UTM54"
author: "Anna Talucci"
date: "2/1/2022"
output: html_document
---

# Overview

This script process landscape/patch statistics by class burned/unburned **For Each patch** for the 2020 fires in Northeastern Siberia. Fires are processed individually.


[Landscapemetrics package details](https://cran.r-project.org/web/packages/landscapemetrics/landscapemetrics.pdf)

 For UTM zone 54 fires


# 1161
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_938.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==938)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj =938) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_938.csv',  row.names = FALSE)
```


# 1027
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1027.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1027)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1027) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1027.csv',  row.names = FALSE)
```



# 1057
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1057.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1057)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1057) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1057.csv',  row.names = FALSE)
```



# 1161
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1161.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1161)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1161) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1161.csv',  row.names = FALSE)
```


# 1166
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1166.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1166)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1166) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1166.csv',  row.names = FALSE)
```


# 1185
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1185.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1185)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 61185) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1185.csv',  row.names = FALSE)
```


# 1228
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1228.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1228)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1228) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1228.csv',  row.names = FALSE)
```


# 1231
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1231.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1231)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1231) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1231.csv',  row.names = FALSE)
```


# 1253
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1253.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1253)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1253) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1253.csv',  row.names = FALSE)
```


# 1262
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1262.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1262)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1262) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1262.csv',  row.names = FALSE)
```


# 1263
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1263.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1263)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1263) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1263.csv',  row.names = FALSE)
```


# 1272
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1272.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1272)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1272) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1272.csv',  row.names = FALSE)
```


# 1282
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1282.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1282)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1282) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1282.csv',  row.names = FALSE)
```


# 1288
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1288.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1288)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1288) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1288.csv',  row.names = FALSE)
```


# 1294
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1294.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1294)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1294) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1294.csv',  row.names = FALSE)
```


# 1303
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1303.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1303)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1303) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1303.csv',  row.names = FALSE)
```


# 1321
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1321.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1321)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1321) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1321.csv',  row.names = FALSE)
```


# 1326
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1326.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1326)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1326) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1326.csv',  row.names = FALSE)
```


# 1337
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1337.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1337)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1337) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1337.csv',  row.names = FALSE)
```


# 1352
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1352.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1352)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1352) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1352.csv',  row.names = FALSE)
```


# 1353
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1353.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1353)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1353) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1353.csv',  row.names = FALSE)
```


# 1354
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1354.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1354)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1354) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1354.csv',  row.names = FALSE)
```


# 1358
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1358.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1358)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1358) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1358.csv',  row.names = FALSE)
```


# 1359
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1359.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1359)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1359) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1359.csv',  row.names = FALSE)
```

# 1374
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1374.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1374)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1374) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1374.csv',  row.names = FALSE)
```


# 1380
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1380.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1380)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1380) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1380.csv',  row.names = FALSE)
```

# 1386
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1386.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1386)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1386) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1386.csv',  row.names = FALSE)
```


# 1388
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1388.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1388)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1388) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1388.csv',  row.names = FALSE)
```

# 1402
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1402.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1402)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1402) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1402.csv',  row.names = FALSE)
```



# 1405
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1405.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1405)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1405) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1405.csv',  row.names = FALSE)
```

# 1420
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1420.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1420)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1420) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1420.csv',  row.names = FALSE)
```


# 1430
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1430.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1430)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1430) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1430.csv',  row.names = FALSE)
```


# 1433
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1433.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1433)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1433) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1433.csv',  row.names = FALSE)
```


# 1438
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1438.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1438)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1438) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1438.csv',  row.names = FALSE)
```


# 1443
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1443.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1443)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1443) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1443.csv',  row.names = FALSE)
```


# 1458
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1458.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1458)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1458) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1458.csv',  row.names = FALSE)
```


# 1465
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1465.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1465)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1465) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1465.csv',  row.names = FALSE)
```


# 1467
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1467.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1467)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1467) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1467.csv',  row.names = FALSE)
```


# 1497
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1497.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1497)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1497) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1497.csv',  row.names = FALSE)
```


# 1503
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1503.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1503)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1503) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1503.csv',  row.names = FALSE)
```


# 1539
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1539.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1539)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1539) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1539.csv',  row.names = FALSE)
```


# 1543
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1543.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1543)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1543) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1543.csv',  row.names = FALSE)
```


# 1552
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1552.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1552)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1552) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1552.csv',  row.names = FALSE)
```


# 1553
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1553.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1553)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1553) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1553.csv',  row.names = FALSE)
```


# 1554
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1554.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1554)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1554) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1554.csv',  row.names = FALSE)
```


# 1559
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1559.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1559)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1559) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1559.csv',  row.names = FALSE)
```


# 1570
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1570.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1570)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1570) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1570.csv',  row.names = FALSE)
```


# 1571
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1571.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1571)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1571) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1571.csv',  row.names = FALSE)
```


# 1575
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1575.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1575)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1575) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1575.csv',  row.names = FALSE)
```


# 1576
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1576.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1576)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1576) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1576.csv',  row.names = FALSE)
```

# 1584
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1584.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1584)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1584) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1584.csv',  row.names = FALSE)
```

# 1608
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1608.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1608)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1608) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1608.csv',  row.names = FALSE)
```

# 1618
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1618.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1618)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1618) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1618.csv',  row.names = FALSE)
```

# 1620
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1620.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1620)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1620) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1620.csv',  row.names = FALSE)
```

# 1636
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1636.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1636)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1636) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1636.csv',  row.names = FALSE)
```

# 1645
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1645.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1645)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1645) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1645.csv',  row.names = FALSE)
```

# 1669
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1669.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1669)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1669) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1669.csv',  row.names = FALSE)
```

# 1696
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1696.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1696)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1696) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1696.csv',  row.names = FALSE)
```

# 1701
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1701.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1701)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1701) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1701.csv',  row.names = FALSE)
```

# 1712
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1712.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1712)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1712) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1712.csv',  row.names = FALSE)
```

# 1716
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1716.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1716)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1716) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1716.csv',  row.names = FALSE)
```

# 1756
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1756.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1756)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1756) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1756.csv',  row.names = FALSE)
```

# 1785
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1785.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1785)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1785) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1785.csv',  row.names = FALSE)
```

# 1796
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1796.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1796)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1796) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1796.csv',  row.names = FALSE)
```

# 1798
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1798.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1798)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1798) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1798.csv',  row.names = FALSE)
```

# 1799
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1799.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1799)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1799) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1799.csv',  row.names = FALSE)
```

# 1807
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1807.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1807)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1807) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1807.csv',  row.names = FALSE)
```

# 1816
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1816.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1816)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1816) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1816.csv',  row.names = FALSE)
```

# 1859
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1859.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1859)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1859) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1859.csv',  row.names = FALSE)
```

# 1896
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1896.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1896)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1896) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1896.csv',  row.names = FALSE)
```

# 1901
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1901.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1901)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1901) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1901.csv',  row.names = FALSE)
```

# 1925
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1925.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1925)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1925) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1925.csv',  row.names = FALSE)
```


# 1935
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1935.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1935)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1935) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1935.csv',  row.names = FALSE)
```


# 1940
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1940.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1940)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1940) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1940.csv',  row.names = FALSE)
```


# 1948
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1948.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1948)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1948) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1948.csv',  row.names = FALSE)
```

# 1993
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_1993.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==1993)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1993) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_1993.csv',  row.names = FALSE)
```

# 2008
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2008.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2008)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2008) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2008.csv',  row.names = FALSE)
```


# 2023
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2023.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2023)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2023) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2023.csv',  row.names = FALSE)
```

# 2037
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2037.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2037)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2037) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2037.csv',  row.names = FALSE)
```


# 2048
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2048.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2048)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2048) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2048.csv',  row.names = FALSE)
```

# 2056
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2056.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2056)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2056) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2056.csv',  row.names = FALSE)
```

# 2059
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2059.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2059)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2059) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2059.csv',  row.names = FALSE)
```

# 2071
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2071.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2071)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2071) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2071.csv',  row.names = FALSE)
```

# 2076
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2076.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2076)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2076) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2076.csv',  row.names = FALSE)
```

# 2086
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2086.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2086)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2086) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2086.csv',  row.names = FALSE)
```

# 2088
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2088.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2088)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2088) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2088.csv',  row.names = FALSE)
```

# 2089
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2089.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2089)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2089) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2089.csv',  row.names = FALSE)
```


# 2089
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2089.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2089)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2089) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2089.csv',  row.names = FALSE)
```

# 2127
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2127.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2127)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2127) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2127.csv',  row.names = FALSE)
```

# 2169
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2169.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2169)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2169) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2169.csv',  row.names = FALSE)
```

# 2232
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2232.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2232)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2232) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2232.csv',  row.names = FALSE)
```

# 2234
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2234.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2234)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2234) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2234.csv',  row.names = FALSE)
```


# 2271
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2271.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2271)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2271) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2271.csv',  row.names = FALSE)
```


# 2283
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2283.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2283)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2283) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2283.csv',  row.names = FALSE)
```



# 2362
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2362.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2362)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2362) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2362.csv',  row.names = FALSE)
```

# 2372
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2372.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2372)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>% 
  mutate(IDobj = 2372) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2372.csv',  row.names = FALSE)
```
# 2389
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2389.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2389)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>% 
  mutate(IDobj = 2389) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2389.csv',  row.names = FALSE)
```

# 2423
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2423.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2423)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2423) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2423.csv',  row.names = FALSE)
```

# 2515
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2515.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2515)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2515) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2515.csv',  row.names = FALSE)
```

# 2547
## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/UTMImagery/BinaryImg_2547.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/FiresUTM/FiresUTM54.shp", "FiresUTM54")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(IDobj==2547)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>% 
  mutate(IDobj = 2547) %>% 
  mutate(UTMZone = 54) %>%
  write.csv(., '../outputs/SummarizePatchesUTM/patchFire_2547.csv',  row.names = FALSE)
```