---
title: "Patch Metrics By fire 2016"
author: "Anna Talucci"
date: "2/19/2022"
output: html_document
---






# Overview

This script process landscape/patch statistics by class burned/unburned **For Each patch** for the 2020 fires in Northeastern Siberia. Fires are processed individually.


[Landscapemetrics package details](https://cran.r-project.org/web/packages/landscapemetrics/landscapemetrics.pdf)



# 117

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_117.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==117)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 117) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_117.csv',  row.names = FALSE)
```


# 239

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_239.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==239)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 239) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_239.csv',  row.names = FALSE)
```

# 247

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_247.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==247)
```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 247) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_247.csv',  row.names = FALSE)
```


# 254

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_254.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==254)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 254) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_254.csv',  row.names = FALSE)
```

# 256

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_256.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==256)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 256) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_256.csv',  row.names = FALSE)
```

# 262

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_262.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==262)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 262) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_262.csv',  row.names = FALSE)
```


# 266

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_266.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==266)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 266) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_266.csv',  row.names = FALSE)
```


# 267

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_267.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==267)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 267) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_267.csv',  row.names = FALSE)
```

# 269

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_269.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==269)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 269) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_269.csv',  row.names = FALSE)
```

# 271

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_271.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==271)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 271) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_271.csv',  row.names = FALSE)
```

# 272

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_272.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==272)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 272) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_272.csv',  row.names = FALSE)
```

# 274

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_274.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==274)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 274) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_274.csv',  row.names = FALSE)
```


# 275

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_275.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==275)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 275) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_275.csv',  row.names = FALSE)
```

# 277

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_277.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==277)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 277) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_277.csv',  row.names = FALSE)
```

# 278

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_278.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==278)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 278) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_278.csv',  row.names = FALSE)
```


# 287

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_287.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==287)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 287) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_287.csv',  row.names = FALSE)
```


# 289

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_289.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==289)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 289) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_289.csv',  row.names = FALSE)
```

#290

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_290.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==290)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj =290) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_290.csv',  row.names = FALSE)
```


# 293

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_293.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==293)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 293) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_293.csv',  row.names = FALSE)
```

# 298

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_298.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==298)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 298) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_298.csv',  row.names = FALSE)
```

# 300

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_300.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==300)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 300) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_300.csv',  row.names = FALSE)
```

# 303

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_303.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==303)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 303) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_303.csv',  row.names = FALSE)
```

# 305

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_305.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==305)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 305) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_305.csv',  row.names = FALSE)
```

# 312

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_312.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==312)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 312) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_312.csv',  row.names = FALSE)
```

# 313

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_313.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==313)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 313) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_313.csv',  row.names = FALSE)
```


# 319

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_319.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==319)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 319) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_319.csv',  row.names = FALSE)
```

# 320

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_320.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==320)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 320) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_320.csv',  row.names = FALSE)
```

# 326

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_326.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==326)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 326) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_326.csv',  row.names = FALSE)
```

# 330

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_330.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==330)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 330) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_330.csv',  row.names = FALSE)
```

# 335

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_335.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==335)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 335) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_335.csv',  row.names = FALSE)
```

# 337

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_337.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==337)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 337) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_337.csv',  row.names = FALSE)
```

# 339

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_339.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==339)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 339) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_339.csv',  row.names = FALSE)
```

# 344

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_344.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==344)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 344) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_344.csv',  row.names = FALSE)
```

# 348

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_348.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==348)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 348) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_348.csv',  row.names = FALSE)
```

# 353

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_353.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==353)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 353) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_353.csv',  row.names = FALSE)
```

# 369

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_369.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==369)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 369) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_369.csv',  row.names = FALSE)
```

# 372

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_372.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==372)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 372) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_372.csv',  row.names = FALSE)
```

# 373

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_373.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==373)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 373) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_373.csv',  row.names = FALSE)
```

# 394

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_394.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==394)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 394) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_394.csv',  row.names = FALSE)
```

# 395

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_395.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==395)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 395) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_395.csv',  row.names = FALSE)
```

# 405

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_405.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==405)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 405) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_405.csv',  row.names = FALSE)
```

# 410

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_410.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==410)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 410) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_410.csv',  row.names = FALSE)
```

# 411

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_411.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==411)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 411) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_411.csv',  row.names = FALSE)
```

# 413

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_413.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==413)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 413) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_413.csv',  row.names = FALSE)
```

# 419

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_419.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==419)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 419) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_419.csv',  row.names = FALSE)
```

# 420

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_420.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==420)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 420) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_420.csv',  row.names = FALSE)
```

# 425

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_425.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==425)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 425) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_425.csv',  row.names = FALSE)
```

# 426

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_426.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==426)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 426) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_426.csv',  row.names = FALSE)
```

# 429

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_429.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==429)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 429) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_429.csv',  row.names = FALSE)
```

# 433

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_433.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==433)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 433) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_433.csv',  row.names = FALSE)
```

# 438

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_438.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==438)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 438) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_438.csv',  row.names = FALSE)
```

# 441

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_441.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==441)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 441) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_441.csv',  row.names = FALSE)
```

# 442

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_442.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==442)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 442) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_442.csv',  row.names = FALSE)
```

# 444

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_444.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==444)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 444) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_444.csv',  row.names = FALSE)
```

# 447

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_447.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==447)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 447) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_447.csv',  row.names = FALSE)
```

# 452

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_452.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==452)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 452) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_452.csv',  row.names = FALSE)
```

# 453

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_453.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==453)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 453) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_453.csv',  row.names = FALSE)
```

# 458

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_458.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==458)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 458) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_458.csv',  row.names = FALSE)
```

# 464

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_464.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==464)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 464) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_464.csv',  row.names = FALSE)
```

# 471

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_471.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==471)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 471) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_471.csv',  row.names = FALSE)
```

# 482

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_482.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==482)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 482) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_482.csv',  row.names = FALSE)
```

# 487

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_487.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==487)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 487) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_487.csv',  row.names = FALSE)
```


# 489

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_489.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==489)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 489) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_489.csv',  row.names = FALSE)
```

# 500

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_500.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==500)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 500) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_500.csv',  row.names = FALSE)
```

# 518

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_518.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==518)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 518) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_518.csv',  row.names = FALSE)
```

# 523

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_523.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==523)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 523) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_523.csv',  row.names = FALSE)
```

# 528

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_528.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==528)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 528) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_528.csv',  row.names = FALSE)
```


# 542

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_542.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==542)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 542) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_542.csv',  row.names = FALSE)
```

# 547

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_547.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==547)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 547) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_547.csv',  row.names = FALSE)
```

# 550

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_550.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==550)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 550) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_550.csv',  row.names = FALSE)
```


# 555

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_555.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==555)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 555) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_555.csv',  row.names = FALSE)
```

# 558

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_558.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==558)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 558) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_558.csv',  row.names = FALSE)
```

# 562

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_562.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==562)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 562) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_562.csv',  row.names = FALSE)
```

# 564

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_564.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==564)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 564) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_564.csv',  row.names = FALSE)
```

# 569

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_569.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==569)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 569) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_569.csv',  row.names = FALSE)
```

# 574

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_574.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==574)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 574) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_574.csv',  row.names = FALSE)
```

# 587

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_587.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==587)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 587) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_587.csv',  row.names = FALSE)
```


# 591

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_591.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==591)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 591) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_591.csv',  row.names = FALSE)
```

# 597

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_597.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==597)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 597) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_597.csv',  row.names = FALSE)
```

# 601

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_601.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==601)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 601) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_601.csv',  row.names = FALSE)
```

# 611

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_611.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==611)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 611) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_611.csv',  row.names = FALSE)
```


# 623

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_623.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==623)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 623) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_623.csv',  row.names = FALSE)
```

# 625

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_625.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==625)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 625) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_625.csv',  row.names = FALSE)
```

# 639

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_639.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==639)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 639) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_639.csv',  row.names = FALSE)
```

# 643

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_643.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==643)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 643) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_643.csv',  row.names = FALSE)
```

# 695

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_695.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==695)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 695) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_695.csv',  row.names = FALSE)
```

# 713

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_713.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==713)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 713) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_713.csv',  row.names = FALSE)
```

# 743

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_743.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==743)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 743) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_743.csv',  row.names = FALSE)
```

# 824

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_824.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==824)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 824) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_824.csv',  row.names = FALSE)
```

# 906

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_906.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==906)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 906) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_906.csv',  row.names = FALSE)
```

# 994

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_994.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==994)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 994) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_994.csv',  row.names = FALSE)
```

# 1005

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_1005.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==1005)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1005) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_1005.csv',  row.names = FALSE)
```

# 1008

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_1008.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==1008)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1008) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_1008.csv',  row.names = FALSE)
```

# 1052

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_1052.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==1052)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1052) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_1052.csv',  row.names = FALSE)
```

# 1101

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_1101.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==1101)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1101) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_1101.csv',  row.names = FALSE)
```

# 1144

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_1144.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==1144)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1144) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_1144.csv',  row.names = FALSE)
```

# 1892

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_1892.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==1892)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 1892) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_1892.csv',  row.names = FALSE)
```

# 2000

## Clear workspace
```{r}
rm(list=ls()) 
```

## Packages
```{r}
library(raster)
library(sp)
library(rgdal)
library(ggplot2)
library(sf)
library(landscapemetrics)
library(dplyr)
```

## Raster
```{r}
r1 <- raster("../data/2016Binary/2016BinaryImg_2000.tif")
```

## Fire perimeters 
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2001-2020.shp", "NESiberiaFires2001-2020")
```

## Select fire perimeter
```{r}
fire1 = fires %>%
  filter(FireYr=="2016") %>%
  filter(IDobj==2000)

```

## Limit Raster to Fire perimeter
```{r}
crop_r1 = mask(r1, fire1)
```

## Define Landscape
```{r}
landscape = crop_r1
```

## Calculate Landscape metrics and export to csv
```{r}
landscape %>% 
  calculate_lsm(.,  what = c("lsm_p_area", "lsm_p_core")) %>%  
  mutate(IDobj = 2000) %>% 
  write.csv(., '../outputs/PatchSummaryEqualArea/2016patchFire_2000.csv',  row.names = FALSE)
```

