---
title: "Subset NE Ecozones"
author: "Anna Talucci"
date: "9/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Overview
This script subsets the global ecozone data to the ecozones of interest.

This code uses the [WWF Ecozones shapefile](https://www.worldwildlife.org/publications/terrestrial-ecoregions-of-the-world). We subset the ecozones for NE Siberia to include the following:


1. Cherskii-Kolyma mountain tundra
2. Northeast Siberia taiga

# Library

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
library(readr)
library(cowplot)
library(ggcorrplot)
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(spatialEco)
```

# Data
```{r}
ecozone = st_read("../data/wwf_ecozone/wwf_terr_ecos_oRn.shp", "wwf_terr_ecos_oRn") 
```

```{r}
head(ecozone)
```

```{r}
biome = ecozone %>% filter(BIOME==11)
```

```{r}
unique(biome$ECO_NAME)
```

# Define Projections

[Equal Area projection for Russia](https://gis.stackexchange.com/questions/264093/projection-for-russia-map)

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 

```{r}
ea_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Select ecozones for region of interest

## Create target of require ecozones 
1. Cherskii-Kolyma mountain tundra (CKMT)
2. Northeast Siberian taiga (NST)
```{r}
target = c("Cherskii-Kolyma mountain tundra", "Northeast Siberian taiga")
```

## Apply filter

Filter for all
```{r}
ne_subset = ecozone %>% 
  filter(ECO_NAME %in% target) %>% 
  mutate(eco_code = ifelse(ECO_NAME %in% "Cherskii-Kolyma mountain tundra", "CKMT", "NST"))
```


## Re-project to equal area
```{r}
ne_subset_ea = st_transform(ne_subset, crs=ea_russia)
```

```{r}
  
ggplot(ne_subset_ea) + geom_sf()
```

## Check data
```{r}
ne_subset
```

```{r}
head(ne_subset)
tail(ne_subset)
```
```{r}
ne_subset$eco_code
```


```{r}
ne_subset %>%
  summarise_all(funs(sum(is.na(.))))
```

```{r}
ne_subset$eco_code
```


## Write Shapefiles

```{r eval=FALSE, include=FALSE}
st_write(ne_subset_ea, "../outputs/EcozonesNE/NstCkmtEcozones.shp", driver="ESRI Shapefile")  
```

